---
title: "Interval Truth Model"
subtitle: "Visualizations of Main Simulation Study, version 1"
author: 
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    embed-resources: true
    fig-width: 7
    fig-height: 4.5
execute:
  message: false
  warning: false
---
# Background
This file contains the visualizations of the first version of the simulation study for the Interval Truth Model (as preregistered). See the main manuscript for our reasons to slightly tweak some aspects of the model. The results of the second iteration of the main simulation study can be found in `src/05_sim_visualizations_v2.Qmd`. 
The results of the preliminary simulation study on the two different link functions can be found in the file `src/05_sim_link_functions_visualizations.Qmd`. 

All errorbars in this document represent $\pm 1$ Monte Carlo Standard Errors.

# Prep
We first load all relevant packages: 

```{r load-pkgs}
packages <- c(
  "tidyverse",
  "SimDesign",
  "rstan",
  "here",
  "posterior",
  "bayesplot",
  "psych",
  "gg4x",
  "ggokabeito",
  "ggExtra",
  "showtext"
)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(packages, update = F, character.only = T)

if(!require("cmdstanr")){
  install.packages("cmdstanr", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
  library(cmdstanr)
}
  
# install.packages("devtools")
# devtools::install_github("teunbrand/ggh4x")

# default chunk options
knitr::opts_chunk$set(
  fig.height = 7,
  fig.width = 10,
  include = TRUE,
  message = FALSE,
  warning = FALSE
)
source(here("src", "00_functions.R"))

# add google font
sysfonts::font_add_google("News Cycle", "news")
# use showtext
showtext::showtext_auto()
```

# Results

The full results of the simulation study are available in two data frames: 

- `sim_res_itm_server.rds`: Results of the simulation study, missing some MSE results due to a small coding error, but containing all information about seed, RAM usage, etc.
- `sim_res_itm_0808.rds`: Resummarized results of the simulation study, now also containing all MSE results as well as more information on divergent transitions.
```{r}
sim_res_itm <- readRDS(
  here(
    "sim_results",
    "sim_results_itm_2024-08-07_08-04-19",
    "resummarized_results_itm.rds"
  )
)
```


Prepare data and convert to long format for plotting: 
```{r}
sim_res_itm_long <- sim_res_itm |> 
  select(!c(contains("conv"), contains("divtrans"), contains("_sd"))) |> 
  # the following columns aren't needed any more for the "resummarized" results
            # "REPLICATIONS", "SIM_TIME", "RAM_USED", "SEED", "COMPLETED", "WARNINGS")) |> 
  # delete "_fn_" from every column name
  rename_all(~str_remove(., "_fn")) |>
  pivot_longer(cols = !c(n_respondents, n_items),
               names_to = "measure", 
               values_to = "value") |> 
  # rename for easier separation
  mutate(measure = str_replace(measure, "abs_bias", "absbias")) |> 
  # remove only the first underscore
  mutate(measure = sub("_", "", measure, fixed = TRUE)) |> 
  separate_wider_delim(measure, 
                       names = c("measure", "summary", "pm", "param"), 
                       delim = "_") |> 
  group_by(n_respondents, n_items, measure, summary, pm) |> 
  pivot_wider(names_from = "param", values_from = "value") |> 
  ungroup() |> 
  mutate(n_respondents = factor(n_respondents))
  
```


## Convergence and Rhat

We now present the average convergence statistics. All values are averages over all replications. A performance measure with a $>$ or a $<$ indicates how many out of 1000 replications had a certain property. For example, $\hat{R} < 1.1$ means that on average, a certain amount of replications had an $\hat{R}$ value below 1.1.
```{r}
# Renaming for the table
name_mapping <- c(
  "rhat_mean" = "$\\hat{R}_{\\text{mean}}$",
  "rhat_prop1c1" = "$\\hat{R} < 1.1$",
  "rhat_prop1c05" = "$\\hat{R} < 1.05$",
  "rhat_prop1c01" = "$\\hat{R} < 1.01$",
  "ess_bulk_mean" = "$\\text{ESS}_{\\text{bulk, mean}}$",
  "ess_bulk_prop100" = "$\\text{ESS}_{\\text{bulk > 100}}$",
  "ess_bulk_prop200" = "$\\text{ESS}_{\\text{bulk > 200}}$",
  "ess_bulk_prop300" = "$\\text{ESS}_{\\text{bulk > 300}}$",
  "ess_tail_mean" = "$\\text{ESS}_{\\text{tail, mean}}$",
  "ess_tail_prop100" = "$\\text{ESS}_{\\text{tail > 100}}$",
  "ess_tail_prop200" = "$\\text{ESS}_{\\text{tail > 200}}$",
  "ess_tail_prop300" = "$\\text{ESS}_{\\text{tail > 300}}$"
)

sim_res_itm |>
  select(contains("conv")) |>
  summarize(across(everything(), mean)) |> 
  # remove "mean_conv." from every column name
  rename_all(~str_remove(., "mean_conv.")) |>
  rename_all(~str_remove(., "mcse_conv.")) |> 
  pivot_longer(cols = everything()) |> 
  # separate mean and mcse based on last underscore
  separate(name, into = c("name", "suffix"), sep = "_(?=[^_]+$)", remove = FALSE) |> 
  pivot_wider(names_from = suffix, values_from = value) |> 
  mutate(mean = round(mean, 4), 
         mcse = round(mcse, 4)) |> 
  mutate(name = name_mapping[name]) |> 
  knitr::kable()
```

Divergent transitions:
```{r}
sim_res_itm |>
  select(contains("divtrans")) |>
  round(3) |> 
  knitr::kable()
```

How many divergent transitions on average in those who had any divergent transitions?
```{r}
sim_res_itm |>
  select(contains("divtrans")) |> 
  rename(divtrans = mean_divtrans.divergent_transitions_mean) |> 
  filter(divtrans != 0) |> 
  summarize(mean_divtrans = mean(divtrans),
            sd_divtrans = sd(divtrans)) |> 
  knitr::kable()
```


How many models with at least one divergent transition per condition:
```{r}
sim_res_itm |>
  select(contains("divtrans"), n_respondents, n_items) |> 
  rename(nonzero_divtrans = nonz_divtrans.divergent_transitions_nonzero) |> 
  select(n_respondents, n_items, nonzero_divtrans) |> 
  knitr::kable()
```



Check if our prespecified MCSE criteria ($<.05$) was fulfilled in all conditions:
```{r}
sim_res_itm |> 
  select(all_of(contains("mcse"))) |> 
  select(all_of(contains("bias"))) |> 
  summarize(across(everything(), max)) |> 
  pivot_longer(cols = everything()) |> 
  knitr::kable()
```




## Visualization

### Absolute Bias of True Location + Width
Here, we show the absolute bias of the true location and width for the different sample sizes and number of items. 

```{r}
plot_sim_absbias <- sim_res_itm_long |>
  filter(pm == "absbias") |>
  filter(summary == "mean") |> 
  filter(measure %in% c("Trinterval", "simplemeaninterval")) |> 
  mutate(measure = case_when(
    measure == "Trinterval" ~ "ITM",
    measure == "simplemeaninterval" ~ "Simple Means"
  )) |>
  mutate(n_items = paste0(n_items, " Items")) |> 
  # order n_items correctly
  mutate(n_items = factor(n_items, levels = c("5 Items", 
                                              "10 Items", 
                                              "20 Items",
                                              "40 Items"))) |>
  ggplot(aes(x = n_respondents, 
             y = mean, 
             color = measure,
             group = measure)) +
  # add vertical line between different sample sizes
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_point(position = position_dodge(0.7), 
             size = 2.5) +
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  ggh4x::facet_wrap2(n_items ~ .,
                     axes = "all",
                     nrow = 1) +
  scale_y_continuous(limits = c(0, .49), expand = c(0,0)) +
  ggokabeito::scale_color_okabe_ito(order = c(5, 1))+
  labs(x = "Number of Respondents",
       y = "Absolute Bias",
       color = "") +
  theme_icm()+
  theme(legend.position = "top",
        text = element_text(size = 22))

# ggsave(here("plots","sim_main", "sim_absbias.pdf"), 
#        plot_sim_absbias, width = 7, height = 3.75)

plot_sim_absbias
```


Here, we focus on the ITM and separate the bias by location and width. 
```{r}
plot_sim_bias_widloc <- sim_res_itm_long |>
  filter(pm == "absbias") |>
  filter(summary == "mean") |> 
  filter(measure %in% c("Trloc", "Trwid")) |> 
  mutate(measure = case_when(
    measure == "Trloc" ~ "Location",
    measure == "Trwid" ~ "Width"
  )) |>
  mutate(n_items = paste0(n_items, " Items")) |> 
  # order n_items correctly
  mutate(n_items = factor(n_items, levels = c("5 Items", 
                                              "10 Items", 
                                              "20 Items",
                                              "40 Items"))) |>
  ggplot(aes(x = n_respondents, 
             y = mean, 
             color = measure,
             group = measure)) +
  # add vertical line between different sample sizes
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_point(position = position_dodge(0.7), 
             size = 2.5) +
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  ggh4x::facet_wrap2(n_items ~ .,
                     axes = "all",
                     nrow = 1) +
  scale_y_continuous(limits = c(0, 0.31), expand = c(0,0)) +
  ggokabeito::scale_color_okabe_ito(order = c(5, 1))+
  labs(x = "Number of Respondents",
       y = "Absolute Bias",
       color = "") +
  theme_icm()+
  theme(legend.position = "top",
        text = element_text(size = 22))

# ggsave(here("plots","sim_main", "sim_absbias_widloc.pdf"), 
#        plot_sim_bias_widloc, width = 7, height = 3.75)

plot_sim_bias_widloc
```



### MSE for Location and Width

Show both ITM and simple means in a comparison: 
```{r}
plot_sim_mse <- sim_res_itm_long |>
  filter(pm == "mse") |>
  filter(summary == "mean") |> 
  filter(measure %in% c("Trinterval", "simplemeaninterval")) |> 
  mutate(measure = case_when(
    measure == "Trinterval" ~ "ITM",
    measure == "simplemeaninterval" ~ "Simple Means"
  )) |>
  mutate(n_items = paste0(n_items, " Items")) |> 
  # order n_items correctly
  mutate(n_items = factor(n_items, levels = c("5 Items", 
                                              "10 Items", 
                                              "20 Items",
                                              "40 Items"))) |>
  ggplot(aes(x = n_respondents, 
             y = mean, 
             color = measure,
             group = measure)) +
  # add vertical line between different sample sizes
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_point(position = position_dodge(0.7), 
             size = 2.5) +
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  ggh4x::facet_wrap2(n_items ~ .,
                     axes = "all",
                     nrow = 1) +
  scale_y_continuous(limits = c(0, .49), expand = c(0,0)) +
  ggokabeito::scale_color_okabe_ito(order = c(5, 1))+
  labs(x = "Number of Respondents",
       y = "MSE",
       color = "") +
  theme_icm()+
  theme(legend.position = "top",
        text = element_text(size = 22))

# ggsave(here("plots","sim_main", "sim_mse.pdf"), 
#        plot_sim_mse, width = 7, height = 3.75)

plot_sim_mse
```



Separated by location and width:
```{r}
plot_sim_mse_widloc <- sim_res_itm_long |>
  filter(pm == "mse") |>
  filter(summary == "mean") |> 
  filter(measure %in% c("Trloc", "Trwid")) |> 
  mutate(measure = case_when(
    measure == "Trloc" ~ "Location",
    measure == "Trwid" ~ "Width"
  )) |>
  mutate(n_items = paste0(n_items, " Items")) |> 
  # order n_items correctly
  mutate(n_items = factor(n_items, levels = c("5 Items", 
                                              "10 Items", 
                                              "20 Items",
                                              "40 Items"))) |>
  ggplot(aes(x = n_respondents, 
             y = mean, 
             color = measure,
             group = measure)) +
  # add vertical line between different sample sizes
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_point(position = position_dodge(0.7), 
             size = 2.5) +
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  ggh4x::facet_wrap2(n_items ~ .,
                     axes = "all",
                     nrow = 1) +
  scale_y_continuous(limits = c(0, 0.11), expand = c(0,0)) +
  ggokabeito::scale_color_okabe_ito(order = c(5, 1))+
  labs(x = "Number of Respondents",
       y = "MSE",
       color = "") +
  theme_icm()+
  theme(legend.position = "top",
        text = element_text(size = 22))

# ggsave(here("plots","sim_main", "sim_mse_widloc.pdf"), 
#        plot_sim_mse_widloc, width = 7, height = 3.75)

plot_sim_mse_widloc
```






### Scatterplot of Location and Width Bias

First write a function that imports the individual estimates of location and width across all results. 
```{r}
prep_locwid <- function(path){
  # list all rds files
  rds_files <- list.files(path, pattern = ".rds", full.names = TRUE)
  
  
  # Function to compare point estimates
  point_comparison <- function(res = res,
                               method = "model",
                               estimate_name,
                               truth_name,
                               summary,
                               pm) {
    tmp_summary <- sapply(res$results, function(x) {
    if(method == "model") {  
      x$fit_summary %>%
        dplyr::filter(stringr::str_detect(variable,
            # ensure that it is at the beginning of the string
            # to avoid issues with a_loc and lambda_loc
            paste0("^", estimate_name))) %>%
        dplyr::select(all_of({{summary}}))
    } else if(method == "simple") {
      x$simple_means %>%
        dplyr::select(all_of({{estimate_name}}))
    }})
    # compare against true parameters
    ret <- list()
    for(i in 1:length(tmp_summary)){
      ret[[i]] <- pm(tmp_summary[[i]], res$results[[i]]$true_parameters[[truth_name]])
    }
    return(ret)
    }
    
  # Function to compute absolute bias
    fn_abs_bias <- function(est_param,
                          true_param,
                          average = TRUE) {
    if (isTRUE(average)) {
      mean(abs(est_param - true_param), na.rm = TRUE)
    } else {
      abs(est_param - true_param)
    }
  }
  
  l_out <- list()
  
  # loop over files to read them in, extracts estimates, computes bias 
  for(i in 1:length(rds_files)){
    # read in rds file
    res <- readRDS(rds_files[i])
    
    # compute inidividual biases
    loc_bias <- point_comparison(res = res,
                                 method = "model",
                                 estimate_name = "Tr_loc",
                                 truth_name = "Tr_loc",
                                 summary = "mean",
                                 pm = fn_abs_bias)
    wid_bias <- point_comparison(res = res,
                                 method = "model",
                                 estimate_name = "Tr_wid",
                                 truth_name = "Tr_wid",
                                 summary = "mean",
                                 pm = fn_abs_bias)
    
    # combine into a data frame
    l_out[[i]] <- data.frame(loc_bias = unlist(loc_bias),
                              wid_bias = unlist(wid_bias),
                              iteration = rep(i, length(loc_bias)))
    
    

  }
  # combine all data frames
  out <- do.call(rbind, l_out)
  return(out)
    
}
```

Then apply the function to the results: 
```{r, eval = FALSE}
locwid_bias <- prep_locwid(here("sim_results" , "sim_results_itm_2024-08-07_08-04-19", "full_sim_results_itm"))
# save the data
saveRDS(
  locwid_bias,
  here(
    "sim_results",
    "sim_results_itm_2024-08-07_08-04-19",
    "locwid_bias.rds"
  )
)
```

```{r}
locwid_bias <- readRDS(here(
  "sim_results",
  "sim_results_itm_2024-08-07_08-04-19",
  "locwid_bias.rds"
))
```



We standardize these values with the true variances from the simulation. We obtain these true values as shown in the `generate_itm_data_sim_study` function:
```{r}
link <- "ilr"
mean_benchmark <- simplex_to_bvn(c(.4, .2, .4), type = link)
sd_benchmark_loc <- simplex_to_bvn(c(.98, .01, .01), type = link)
sd_benchmark_wid <- simplex_to_bvn(c(.495, .01, .495), type = link)
    
# mean for Tr_loc
mu_Tr_loc <- mean_benchmark[1]
# mean for Tr_wid
mu_Tr_wid <- mean_benchmark[2]
# SD forTr_loc
sigma_Tr_loc <- sd_benchmark_loc[1] / 4
# SD Tr_wid
sigma_Tr_wid <- abs(sd_benchmark_wid[2] - mean_benchmark[2]) / 4

# Then standardize the values
locwid_bias <- locwid_bias |> 
  dplyr::mutate(loc_bias_std = loc_bias / sigma_Tr_loc,
                wid_bias_std = wid_bias / sigma_Tr_wid)


```


Then create a scatterplot to investigate compensatory behavior, in other words, if the bias of the location is higher when the bias of the width is lower and vice versa. Overall, there does not seem to be strong evidence for compensatory behavior.
```{r}
# if fonts aren't working properly with ggExtra
# extrafont::font_import()

# # add google font
sysfonts::font_add_google("News Cycle", "news")
# use showtext
showtext::showtext_auto()
# windows()
# extrafont::font_import(pattern = "NewsCycle-Regular.ttf")
# extrafont::loadfonts()

scatter_tmp <- locwid_bias |> 
  ggplot(aes(x = loc_bias_std, y = wid_bias_std)) +
  geom_point(alpha = 0.5) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  labs(x = "Location Bias (standardized)",
       y = "Width Bias (standardized)") +
  geom_smooth(method = "loess", se = TRUE) +
  scale_x_continuous(limits = c(0, .85), expand = c(0,0)) +
  scale_y_continuous(limits = c(0, .85), expand = c(0,0)) +
  # manually set theme here due to font conflicts
  ggplot2::theme_minimal(base_family = "news") +
  ggplot2::theme(
      # remove minor grid
      panel.grid.minor = ggplot2::element_blank(),
      # Title and Axis Texts
      plot.title = ggplot2::element_text(face = "plain",
                                         size = ggplot2::rel(1.2),
                                         hjust = 0.5),
      plot.subtitle = ggplot2::element_text(size = ggplot2::rel(1.1),
                                            hjust = 0.5),
      axis.text.x = ggplot2::element_text(face = "plain", size = ggplot2::rel(1.05)),
      axis.text.y = ggplot2::element_text(face = "plain", size = ggplot2::rel(1.05)),
      axis.title.x = ggplot2::element_text(face = "plain", size = ggplot2::rel(1.3)),
      axis.title.y = ggplot2::element_text(face = "plain", size = ggplot2::rel(1.3)),
      axis.line = element_line(colour = "#6d6d6e"),
      
      # Faceting
      strip.text = ggplot2::element_text(face = "plain",
                                         size = ggplot2::rel(1.1),
                                         hjust = 0.5),
      strip.text.x.top = ggplot2::element_text(face = "plain", 
                                               size = ggplot2::rel(1.2),
                                               hjust = 0.5),
      # strip.text.y = element_blank(),
      strip.background = ggplot2::element_rect(fill = NA, color = NA),
      # Grid
      panel.grid = ggplot2::element_line(colour = "#F3F4F5"),
      # Legend
      legend.title = ggplot2::element_text(face = "plain"),
      legend.position = "top",
      legend.justification = 1,
      # Panel/Facets
      panel.spacing.x = ggplot2::unit(1.6, "lines"),
      panel.spacing.y = ggplot2::unit(1.6, "lines"),
      # Remove vertical grid lines
      panel.grid.major.x = ggplot2::element_blank())+
  theme(text = element_text(size = 22))

# show marginal distributions as histograms
# doesn't work with custom font
# scatter_locwid <- ggExtra::ggMarginal(scatter_tmp, type = "histogram", bins = 50)+
#   theme_minimal(base_family = "news")

# ggsave(here("plots","sim_main", "scatter_locwid.pdf"), 
#        scatter_tmp, width = 7, height = 5)

scatter_tmp
```


### Summary Table
To show the numerical results of the main outcome measures, we create a summary table below.
```{r}
sim_res_itm |> 
  select(n_items, n_respondents, 
         Tr_interval_mean_fn_abs_bias_mean, Tr_interval_mean_fn_abs_bias_mcse,
         Tr_interval_mean_fn_mse_mean, Tr_interval_mean_fn_mse_mcse, 
         simplemean_interval_mean_fn_abs_bias_mcse, simplemean_interval_mean_fn_abs_bias_mean,
         simplemean_interval_mean_fn_mse_mean, simplemean_interval_mean_fn_mse_mcse) |> 
  pivot_longer(cols = !c(n_items, n_respondents)) |> 
  # split based on last underscore 
  separate(name, into = c("name", "suffix"), sep = "_(?=[^_]+$)", remove = FALSE) |> 
  pivot_wider(names_from = suffix, values_from = value) |> 
  # again split based on last underscore
  separate(name, into = c("name", "pm"), sep = "_(?=[^_]+$)", remove = FALSE) |> 
  # remove "mean_fn" from name
  mutate(name = str_remove(name, "_mean_fn_abs")) |> 
  mutate(name = str_remove(name, "_mean_fn")) |> 
  dplyr::rename(
    "Items" = "n_items",
    "Respondents" = "n_respondents",
    "Model" = "name",
    "Measure" = "pm",
    "Mean" = "mean",
    "MCSE" = "mcse"
  ) |> 
  mutate(Model = case_when(
    Model == "Tr_interval" ~ "ITM",
    Model == "simplemean_interval" ~ "Simple Means"
  )) |> 
  mutate(Measure = case_when(
    Measure == "bias" ~ "Bias",
    Measure == "mse" ~ "MSE"
  )) |> 
  mutate(across(c(Mean, MCSE), ~round(., 4))) |> 
  knitr::kable()
  

```


# Session Info

```{r}
pander::pander(sessionInfo())
```


