---
title: "Interval Truth Model"
subtitle: "Simulation Study: Development of Data Generating Process - Stick-Breaking Transformation"
author: 
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    embed-resources: true
execute:
  message: false
  warning: false
params: 
  refit: false
---

```{r setup, include = FALSE}
# Libraries
packages <- c(
  "tidyverse",
  "yardstick",
  "readxl",
  "cmdstanr",
  "bayesplot",
  "posterior",
  "bayestestR",
  "rmarkdown",
  "cowplot",
  "svglite",
  "psych",
  "here",
  "ggpubr"
)
# in case cmdstanr is not installed
# install.packages("cmdstanr",
#                  repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

if (!require("pacman"))
  install.packages("pacman")
pacman::p_load(packages, update = F, character.only = T)

# default chunk options
knitr::opts_chunk$set(
  fig.height = 7,
  fig.width = 10,
  include = TRUE,
  message = FALSE,
  warning = FALSE
)
source(here("src", "00_functions.R"))
set.seed(35032)
```


# Check simulation settings

## Define Parameter Bounds for Variances
```{r}
# compute a benchmark for the mean and SD of the parameters
mean_benchmark <- simplex_to_bvn(c(.425, .15, .425), type = "sb")
sd_benchmark_loc <- simplex_to_bvn(c(.98, .01, .01), type = "sb")
sd_benchmark_wid <- simplex_to_bvn(c(.495, .01, .495), type = "sb")
# mean for Tr_loc
mu_Tr_loc <- mean_benchmark[1]
mu_Tr_loc %>% round(2)
# mean for Tr_wid
mu_Tr_wid <- mean_benchmark[2]
mu_Tr_wid %>% round(2)
# SD forTr_loc
sigma_Tr_loc <- sd_benchmark_loc[1] / 4
sigma_Tr_loc %>% round(2)
# SD Tr_wid
sigma_Tr_wid <- abs(sd_benchmark_wid[2] - mean_benchmark[2]) / 4
sigma_Tr_wid %>% round(2)

# SDs for other parameters
sigma_lambda_E_loc <- .3
sigma_lambda_E_loc %>% round(2)
sigma_lambda_E_wid <- .3
sigma_lambda_E_wid %>% round(2)
sigma_a_loc <- .3
sigma_b_loc <- sigma_Tr_loc / 3
sigma_b_loc %>% round(2)
sigma_b_wid <- sigma_Tr_wid / 3
sigma_b_wid %>% round(2)

# sigma_lambda_E_loc <- sigma_Tr_loc / 3
# sigma_lambda_E_loc
# sigma_lambda_E_wid <- sigma_Tr_wid / 3
# sigma_lambda_E_wid
# sigma_a_loc <- sigma_Tr_loc / 3
# sigma_b_loc <- sigma_Tr_loc / 3
# sigma_b_loc
# sigma_b_wid <- sigma_Tr_wid / 3
# sigma_b_wid
```

## Simulate 100 Datasets
```{r}
sim_data_list <- map(1:100, ~ {
  generate_itm_data_sim_study(
    n_respondents = 50,
    n_items = 50,
    link = "sb",
    mu_Tr_loc = mu_Tr_loc,
    mu_Tr_wid = mu_Tr_wid,
    sigma_Tr_loc = sigma_Tr_loc,
    sigma_Tr_wid = sigma_Tr_wid,
    sigma_lambda_E_loc = sigma_lambda_E_loc,
    sigma_lambda_E_wid = sigma_lambda_E_wid,
    sigma_a_loc = sigma_a_loc,
    sigma_b_loc = sigma_b_loc,
    sigma_b_wid = sigma_b_wid
  )
})
```

## Plots
### True Intervals
```{r}
true_intervals <- 
  map_dfr(sim_data_list, 
         .f = ~.x$parameters[c("Tr_L", "Tr_U")] %>%
          do.call(cbind.data.frame,.)) %>%
  mutate(Tr_loc = Tr_L + (Tr_U - Tr_L) / 2,
         Tr_wid = Tr_U - Tr_L)

true_intervals %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 2, slope = -2) +
  geom_point(
    aes(x = Tr_loc, y = Tr_wid),
    size = 1.5,
    alpha = .1,
    shape = 16
  )+
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
    scale_y_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14)
```

```{r}
samples <- gather_values(
  lower = true_intervals$Tr_L,
  upper = true_intervals$Tr_U,
  item_id = 1:nrow(true_intervals),
  step_size = 0.01
)
samples %>%
  ggplot(aes(x = samples)) +
  geom_density(fill = "purple", alpha = .5) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```

### Response Data
```{r}
responses <- map_dfr(sim_data_list, ~ .x$responses) %>%
  mutate(X_loc = x_L + (x_U - x_L) / 2, 
         X_wid = x_U - x_L)

samples <- gather_values(
  lower = responses$x_L,
  upper = responses$x_U,
  item_id = responses$jj,
  step_size = 0.01
)

# density plot
samples %>% 
  ggplot(aes(x = samples)) +
  geom_density(fill = "purple", alpha = .5) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```

```{r}
responses %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 2, slope = -2) +
  geom_point(
    aes(x = X_loc, y = X_wid),
    size = .05,
    alpha = .1,
    shape = 16
  ) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14)

ggsave(here("plots", "response_data_sb_fixed.pdf"))
```

### Item Parameters
```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["lambda_loc"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = 1/lambda_loc),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) 
```

```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["lambda_wid"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = 1/lambda_wid),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
  theme_pubr(base_size = 14)
```


### Person Parameters
```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["E_loc"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = 1/E_loc),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) 
```

```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["E_wid"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = 1/E_wid),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) 
```

```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["a_loc"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = a_loc),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) 
```

```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["b_loc"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = b_loc),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) 
```

```{r}
map_dfr(sim_data_list, 
        ~ .x$parameters["b_wid"] %>%
          data.frame()) %>%
  ggplot() +
  geom_histogram(
    aes(x = b_wid),binwidth = .02, fill = "purple", alpha = .7
  )+
  scale_x_continuous(
    expand = expansion()
  ) +
    scale_y_continuous(
    expand = expansion()
  ) +
    theme_pubr(base_size = 14) 
```

***

# Generate Data for One Replication
```{r}
n_respondents <- 50
n_items <- 50

sim_data <-
  generate_itm_data_sim_study(
    n_respondents = n_respondents,
    n_items = n_items,
    link = "sb",
    mu_Tr_loc = mu_Tr_loc,
    mu_Tr_wid = mu_Tr_wid,
    sigma_Tr_loc = sigma_Tr_loc,
    sigma_Tr_wid = sigma_Tr_wid,
    sigma_lambda_E_loc = sigma_lambda_E_loc,
    sigma_lambda_E_wid = sigma_lambda_E_wid,
    sigma_a_loc = sigma_a_loc,
    sigma_b_loc = sigma_b_loc,
    sigma_b_wid = sigma_b_wid
  )
responses <- sim_data$responses
```

## Plot Data
```{r} 
samples <- gather_values(
  lower = responses$x_L,
  upper = responses$x_U,
  item_id = responses$jj,
  step_size = 0.01
)
samples %>% 
  ggplot(aes(x = samples)) +
  geom_density(fill = "purple", alpha = .5) +
  facet_wrap(~item_id) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())

```

## Plot True Intervals as Densities
```{r}
gather_values(
  lower = sim_data$parameters$Tr_L,
  upper = sim_data$parameters$Tr_U,
  item_id = 1,
  step_size = 0.01
) %>% 
  ggplot(aes(x = samples)) +
  geom_density(fill = "purple", alpha = .5) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```

## Plot True Intervals as Error Bars
```{r}
data.frame(
  idx = 1:n_items,
  lower = sim_data$parameters$Tr_L,
  upper = sim_data$parameters$Tr_U
) %>%
  ggplot(aes(y = idx)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.3) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = seq(0, 1, .25),
    expand = expansion()
  ) +
  labs(x = "Latent Truth",
       y = "Item") +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```

## Plot True Intervals as Ternary Plot
```{r}
data.frame(
  idx = 1:n_items,
  Tr_L = sim_data$parameters$Tr_L,
  Tr_U = sim_data$parameters$Tr_U) %>% 
  mutate(
  Tr_loc = Tr_L + (Tr_U - Tr_L) / 2,
  Tr_wid = Tr_U - Tr_L
) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 2) +
  geom_abline(intercept = 2, slope = -2) +
  geom_point(
    aes(x = Tr_loc, y = Tr_wid),
    size = 4,
    alpha = .5,
    shape = 16
  )+
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
    scale_y_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  theme_pubr(base_size = 14)
```

***

# Fit Model With "SB"-Link Function

## Stan Data
```{r}
### Stan data declaration
I <- length(unique(responses$ii))
J <- length(unique(responses$jj))
N <- nrow(responses)
ii <- responses$ii
jj <- responses$jj
nn <- c(1:N)
Y_splx <- cbind(responses$x_splx_1, responses$x_splx_2, responses$x_splx_3) %>%
  as.matrix()

Y_splx[is.na(Y_splx)]

# sanity check: all rows sum to 1
# check <- apply(Y_splx, 1, sum) %>% as.data.frame()
# table(check)

## stan data list
stan_data_sb <- list(
  I = I,
  J = J,
  N = N,
  ii = ii,
  jj = jj,
  nn = nn,
  Y_splx = Y_splx,
  link = 2 # sb
)
```

## Compile Model
```{r}
# Choose model to fit
model_name <- "itm_simulation"
# Compile model
model <-
  cmdstanr::cmdstan_model(
    stan_file = here("src", "models", paste0(model_name, ".stan")),
    pedantic = TRUE,
    quiet = FALSE
  )
```

## Run Sampler
```{r eval=FALSE}
#| eval: !expr params$refit


# number of MCMC chains
n_chains <- 4
# Run sampler
fit_sb <- model$sample(
  data = stan_data_sb,
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 500,
  thin = 1,
  adapt_delta = .9,
  init = .1
)
# save fit
fit_sb$save_object(file =  here("fits", paste0(model_name, "_fit_sb.RDS")))
```

```{r}
# load  fit
fit_sb <- readRDS(file =  here("fits", paste0(model_name, "_fit_sb.RDS")))
```

***

### Get Estimates
```{r}
estimates_summary <- fit_sb$summary()
```

### Sampler Diagnostics
```{r}
# sampler diagnostics
fit_sb$sampler_diagnostics(format = "df") %>% 
  psych::describe(quant = c(.05,.95),) %>%
  round(2) %>%  
  as.data.frame() %>% 
  dplyr::select(median, min, Q0.05, Q0.95,  max) %>% 
  .[-c(7:9),]
```

```{r}
# convergence diagnostics
convergence_summary <- 
  fit_sb$draws(format = "df") %>%
  summarise_draws(.x = ., "rhat", "ess_bulk", "ess_tail") %>%
  remove_missing() %>%
  select(-variable) %>%
  psych::describe(., quant = c(.05, .95)) %>%
  as.data.frame() %>%
  select(median, Q0.05, Q0.95, min, max)

convergence_summary %>% round(3)
```

### Effective sample size (ESS) & Rhat Plots
```{r message=FALSE, warning=FALSE}
# color scheme
color_scheme_set(scheme = "purple")

# Effective sample sizes
plot_neff <-
  mcmc_neff_hist(bayesplot::neff_ratio(fit_sb), binwidth = .01) +
  labs(title = "A") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  )
# Rhat
plot_rhat <-
  bayesplot::mcmc_rhat_hist(bayesplot::rhat(fit_sb)) +
  labs(title = "B") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  ) +
  yaxis_text(on = TRUE)

# Combined plot
plot_diagnostics <- gridExtra::grid.arrange(plot_neff, plot_rhat, ncol = 2)
```

## Parameter Plots
```{r}
# color scheme
color_scheme_set(scheme = "purple")

true_parameters <- sim_data$parameters
```

### Person Competence: Location
```{r }
plot_E_loc <-
  mcmc_recover_scatter(x = fit_sb$draws("E_loc"), true = true_parameters$E_loc) +
  labs(
    subtitle = "Person Competence: Location",
  ) 
plot_E_loc
```

### Person Competence: Width
```{r }
plot_E_wid <-
  mcmc_recover_scatter(x = fit_sb$draws("E_wid"), true = true_parameters$E_wid) +
  labs(subtitle = "Person Competence: Width")
plot_E_wid
```

### Person Scaling Bias: Location
```{r }
plot_a_loc <-
  mcmc_recover_scatter(x = fit_sb$draws("a_loc"), true = true_parameters$a_loc) +
  labs(subtitle = "Person Scaling Bias: Location")
plot_a_loc
```

### Person Shifting Bias: Location
```{r }
plot_b_loc <-
  mcmc_recover_scatter(x = fit_sb$draws("b_loc"), true = true_parameters$b_loc) +
  labs(subtitle = "Person Shifting Bias: Location") 
plot_b_loc
```

### Person Shifting Bias: Width
```{r }
plot_b_wid <-
  mcmc_recover_scatter(x = fit_sb$draws("b_wid"), true = true_parameters$b_wid) +
  labs(subtitle = "Person Shifting Bias: Width")
plot_b_wid
```

### Item Discernability: Location
```{r }
plot_lambda_loc <-
  mcmc_recover_scatter(x = fit_sb$draws("lambda_loc"),
                       true = true_parameters$lambda_loc)
plot_lambda_loc
```

### Item Discernability: Width
```{r }
# plot
plot_lambda_wid <-
  mcmc_recover_scatter(x = fit_sb$draws("lambda_wid"),
                       true = true_parameters$lambda_wid) +
  labs(subtitle = "Item Discernability: Width")
plot_lambda_wid
```

### Latent Truth Intervals
```{r }
# plot
plot_Tr_loc <-
  mcmc_recover_scatter(x = fit_sb$draws("Tr_loc"),
                       true = true_parameters$Tr_loc)
plot_Tr_loc
```

```{r }
# plot
plot_Tr_wid <-
  mcmc_recover_scatter(x = fit_sb$draws("Tr_wid"),
                       true = true_parameters$Tr_wid) +
  labs(subtitle = "Item True Width")

plot_Tr_wid
```

```{r}
# ITM estimates
latent_truth_est_sb <- data.frame(
  idx = 1:J,
  type = "estimated",
  Tr_L_est = fit_sb$summary("Tr_splx") %>% 
    as.data.frame() %>% 
    pull(median) %>% 
    .[1:J],
  Tr_wid_est = fit_sb$summary("Tr_splx") %>% 
    as.data.frame() %>% 
    pull(median) %>% 
    .[(J + 1):(J * 2)]
) %>%
  mutate(Tr_loc_est = Tr_L_est + Tr_wid_est / 2, 
         Tr_U_est = Tr_L_est + Tr_wid_est)

# compute means in the unbounded space
means_sb <-
  cbind(jj, simplex_to_bvn(Y_splx, type = "sb")) %>%
  as.data.frame() %>%
  dplyr::group_by(jj) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::select(-jj) %>%
  bvn_to_simplex(type = "sb") %>%
  mutate(
    idx = 1:J,
    type = "simple_mean",
    Tr_L_sm = x_1,
    Tr_U_sm = 1 - x_3
  ) %>%
  select(-c(x_1, x_2, x_3))


# true parameters
latent_truth_true <- data.frame(
  idx = 1:J,
  type = "true",
  Tr_L_true = true_parameters$Tr_L,
  Tr_U_true = true_parameters$Tr_U
)

df_interval_plot_sb <- full_join(latent_truth_est_sb, latent_truth_true) %>%
  full_join(means_sb) %>% 
  mutate(type = factor(type, levels = c("estimated", "true")))
```

#### Interval Plot
```{r message=FALSE, warning=FALSE}
cols <- c("True" = "grey70", "ITM"="red","Mean"="blue")

df_interval_plot_sb %>%
  ggplot(aes(y = idx)) +
    geom_errorbarh(
    aes(xmin = Tr_L_true, xmax = Tr_U_true, col = "True"), 
    height = 0,
    linewidth = 5,
  ) +
  geom_errorbarh(
    aes(xmin = Tr_L_sm, xmax = Tr_U_sm, col = "Mean"),
    height = 0,
    linewidth = 3,
    alpha = .4
  ) +
  geom_errorbarh(
    aes(xmin = Tr_L_est, xmax = Tr_U_est, col = "ITM"),
    height = 0,
    linewidth = 2,
    alpha = .5
    ) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = seq(0, 1, .25),
    expand = expansion()
  ) +
    scale_y_discrete(
    expand = expansion(add = 1)
  ) +
scale_color_manual(values = cols) +
  labs(x = "Latent Truth", y = "Item") +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```

# cross-Fit Model With ILR-Logit Function

## Stan Data
```{r}
stan_data_ilr <- list(
  I = I,
  J = J,
  N = N,
  ii = ii,
  jj = jj,
  nn = nn,
  Y_splx = Y_splx,
  link = 1 # ilr
)
```

## Run Sampler
```{r eval=FALSE}
#| eval: !expr params$refit


# number of MCMC chains
n_chains <- 4
# Run sampler
fit_ilr <- model$sample(
  data = stan_data_ilr,
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 500,
  thin = 1,
  adapt_delta = .9,
  init = .1
)
# save fit
fit_ilr$save_object(file =  here("fits", paste0(model_name, "_fit_ilr_cross.RDS")))
```

```{r}
# load  fit_ilr
fit_ilr <- readRDS(file =  here("fits", paste0(model_name, "_fit_ilr_cross.RDS")))
```

***

### Get Estimates
```{r}
estimates_summary <- fit_ilr$summary()
```

### Sampler Diagnostics
```{r}
# sampler diagnostics
fit_ilr$sampler_diagnostics(format = "df") %>% 
  psych::describe(quant = c(.05,.95),) %>%
  round(2) %>%  
  as.data.frame() %>% 
  dplyr::select(median, min, Q0.05, Q0.95,  max) %>% 
  .[-c(7:9),]
```

```{r}
# convergence diagnostics
convergence_summary <- 
  fit_ilr$draws(format = "df") %>%
  summarise_draws(.x = ., "rhat", "ess_bulk", "ess_tail") %>%
  remove_missing() %>%
  select(-variable) %>%
  psych::describe(., quant = c(.05, .95)) %>%
  as.data.frame() %>%
  select(median, Q0.05, Q0.95, min, max)

convergence_summary %>% round(3)
```

### Effective sample size (ESS) & Rhat Plots
```{r message=FALSE, warning=FALSE}
# color scheme
color_scheme_set(scheme = "purple")

# Effective sample sizes
plot_neff <-
  mcmc_neff_hist(bayesplot::neff_ratio(fit_ilr), binwidth = .01) +
  labs(title = "A") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  )
# Rhat
plot_rhat <-
  bayesplot::mcmc_rhat_hist(bayesplot::rhat(fit_ilr)) +
  labs(title = "B") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  ) +
  yaxis_text(on = TRUE)

# Combined plot
plot_diagnostics <- gridExtra::grid.arrange(plot_neff, plot_rhat, ncol = 2)
```

## Parameter Plots
```{r}
# color scheme
color_scheme_set(scheme = "purple")

true_parameters <- sim_data$parameters
```

### Person Competence: Location
```{r }
plot_E_loc <-
  mcmc_recover_scatter(x = fit_ilr$draws("E_loc"), true = true_parameters$E_loc) +
  labs(
    subtitle = "Person Competence: Location",
  ) 
plot_E_loc
```

### Person Competence: Width
```{r }
plot_E_wid <-
  mcmc_recover_scatter(x = fit_ilr$draws("E_wid"), true = true_parameters$E_wid) +
  labs(subtitle = "Person Competence: Width")
plot_E_wid
```

### Person Scaling Bias: Location
```{r }
plot_a_loc <-
  mcmc_recover_scatter(x = fit_ilr$draws("a_loc"), true = true_parameters$a_loc) +
  labs(subtitle = "Person Scaling Bias: Location")
plot_a_loc
```

### Person Shifting Bias: Location
```{r }
plot_b_loc <-
  mcmc_recover_scatter(x = fit_ilr$draws("b_loc"), true = true_parameters$b_loc) +
  labs(subtitle = "Person Shifting Bias: Location") 
plot_b_loc
```

### Person Shifting Bias: Width
```{r }
plot_b_wid <-
  mcmc_recover_scatter(x = fit_ilr$draws("b_wid"), true = true_parameters$b_wid) +
  labs(subtitle = "Person Shifting Bias: Width")
plot_b_wid
```

### Item Discernability: Location
```{r }
plot_lambda_loc <-
  mcmc_recover_scatter(x = fit_ilr$draws("lambda_loc"),
                       true = true_parameters$lambda_loc)
plot_lambda_loc
```

### Item Discernability: Width
```{r }
# plot
plot_lambda_wid <-
  mcmc_recover_scatter(x = fit_ilr$draws("lambda_wid"),
                       true = true_parameters$lambda_wid) +
  labs(subtitle = "Item Discernability: Width")
plot_lambda_wid
```

### Latent Truth Intervals
```{r }
# plot
plot_Tr_loc <-
  mcmc_recover_scatter(x = fit_ilr$draws("Tr_loc"),
                       true = true_parameters$Tr_loc) +
  labs(subtitle = "Item True Location")
plot_Tr_loc
```

```{r }
# plot
plot_Tr_wid <-
  mcmc_recover_scatter(x = fit_ilr$draws("Tr_wid"),
                       true = true_parameters$Tr_wid) +
  labs(subtitle = "Item True Width")

plot_Tr_wid
```

```{r}
# ITM estimates
latent_truth_est_ilr <- data.frame(
  idx = 1:J,
  type = "estimated",
  Tr_L_est = fit_ilr$summary("Tr_splx") %>% 
    as.data.frame() %>% 
    pull(median) %>% 
    .[1:J],
  Tr_wid_est = fit_ilr$summary("Tr_splx") %>% 
    as.data.frame() %>% 
    pull(median) %>% 
    .[(J + 1):(J * 2)]
) %>%
  mutate(Tr_loc_est = Tr_L_est + Tr_wid_est / 2, 
         Tr_U_est = Tr_L_est + Tr_wid_est)

# compute means in the unbounded space
means_ilr <-
  cbind(jj, simplex_to_bvn(Y_splx), type = "ilr") %>%
  as.data.frame() %>%
  dplyr::group_by(jj) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::select(-jj) %>%
  bvn_to_simplex(type = "ilr") %>%
  mutate(
    idx = 1:J,
    type = "simple_mean",
    Tr_L_sm = x_1,
    Tr_U_sm = 1 - x_3
  ) %>%
  select(-c(x_1, x_2, x_3))

df_interval_plot_ilr <- full_join(latent_truth_est_ilr, latent_truth_true) %>%
  full_join(means_ilr) %>% 
  mutate(type = factor(type, levels = c("estimated", "true")))
```

#### Interval Plot
```{r message=FALSE, warning=FALSE}
cols <- c("ITM (ILR - cross)" = "red", "Mean" = "blue")

df_interval_plot_ilr %>%
  ggplot(aes(y = idx)) +
    geom_errorbarh(
    aes(xmin = Tr_L_true, xmax = Tr_U_true), 
    height = 0,
    linewidth = 5,
    col = "grey80"
  ) +
  geom_errorbarh(
    aes(xmin = Tr_L_sm, xmax = Tr_U_sm, colour = "Mean"),
    height = 0,
    linewidth = 3,
    alpha = .4
  ) +
  geom_errorbarh(
    aes(xmin = Tr_L_est, xmax = Tr_U_est, colour = "ITM (ILR - cross)"),
    height = 0,
    linewidth = 2,
    alpha = .5
    ) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = seq(0, 1, .25),
    expand = expansion()
  ) +
    scale_y_discrete(
    expand = expansion(add = 1)
    ) +
  scale_colour_manual(name = "Model", values = cols) +
  labs(x = "Latent Truth", y = "Item")+
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```

### Comparison of ILR and SB Estimates
```{r}
df_interval_plot_comparison <-
  full_join(
    latent_truth_est_sb %>%
      rename(
        Tr_L_est_sb = Tr_L_est,
        Tr_wid_est_sb = Tr_wid_est,
        Tr_loc_est_sb = Tr_loc_est,
        Tr_U_est_sb = Tr_U_est
      ),
    latent_truth_est_ilr %>%
      rename(
        Tr_L_est_ilr = Tr_L_est,
        Tr_U_est_ilr = Tr_U_est,
        Tr_wid_est_ilr = Tr_wid_est,
        Tr_loc_est_ilr = Tr_loc_est
      )
  ) %>%
  full_join(latent_truth_true) %>%
  mutate(type = factor(type, levels = c("estimated", "true")))
```

```{r message=FALSE, warning=FALSE}
cols <- c(
  "True" = "grey70",
  "SB (self)" = "blue",
  "ILR (cross)" = "red"
)

df_interval_plot_comparison %>%
  ggplot(aes(y = idx)) +
  geom_errorbarh(
    aes(xmin = Tr_L_true, xmax = Tr_U_true, col = "True"),
    height = 0,
    linewidth = 5
  ) +
  geom_errorbarh(
    aes(
      xmin = Tr_L_est_sb,
      xmax = Tr_U_est_sb,
      colour = "SB (self)"
    ),
    height = 0,
    linewidth = 3,
    alpha = .4
  ) +
  geom_errorbarh(
    aes(
      xmin = Tr_L_est_ilr,
      xmax = Tr_U_est_ilr,
      colour = "ILR (cross)"
    ),
    height = 0,
    linewidth = 2,
    alpha = .5
  ) +
  scale_y_discrete(expand = expansion(add = 1)) +
  scale_color_manual(values = cols) +
  labs(x = "Latent Truth", y = "Item") +
  theme_pubr(base_size = 14) +
  theme(plot.margin = margin(.1, .5, .1, .1, "cm"),
        panel.grid.major = element_line())
```