---
title: "Interval Truth Model"
subtitle: "Empirical Example: Verbal Quantifiers"
author: 
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    embed-resources: true
execute:
  message: false
  warning: false
params: 
  refit: false
---

```{r setup, include = FALSE}
# Libraries
packages <- c(
  "quarto",
  "tidyverse",
  "yardstick",
  "readxl",
  "cmdstanr",
  "bayesplot",
  "bayesTestR",
  "posterior",
  "bayestestR",
  "rmarkdown",
  "cowplot",
  "svglite",
  "psych",
  "here",
  "ggpubr",
  "ggokabeito",
  "ggh4x",
  "ggtext"
)
# in case cmdstanr is not installed
# install.packages("cmdstanr",
#                  repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

if (!require("pacman")) install.packages("pacman") 
pacman::p_load(packages, update = F, character.only = T)
source("00_functions.R")
```

# Load Data
```{r}
### Load Data
df_long <- read_rds(here("data", "interval_multi_apps_long.rds"))

# item names
item_names_quantifier <- df_long %>% 
  dplyr::select(jj, name_en) %>% 
  distinct() %>% 
  arrange(jj) %>% 
  pull(name_en)
```

## Stan Data
```{r}
### Stan data declaration
df_long <- df_long %>% dplyr::filter(!is.na(x_splx_1))

I = length(unique(df_long$ii))
J = length(unique(df_long$jj))
N  = nrow(df_long)
ii = df_long$ii
jj = df_long$jj
nn = c(1:N)
Y_splx = cbind(df_long$x_splx_1,
           df_long$x_splx_2,
           df_long$x_splx_3) %>% 
  as.matrix()

#Y_splx[is.na(Y_splx)]

# # sanity check: all rows sum to 1
# check <- apply(Y_splx, 1, sum) %>% as.data.frame()
# table(check)

## stan data list
stan_data <- list(
  I = I,
  J = J,
  N = N,
  ii = ii,
  jj = jj,
  nn = nn,
  Y_splx = Y_splx
)

# Choose model to fit
model_name <- "itm_beta"
```

# Fit Full Model

We first fit the full model to the verbal quantifier data to see what the 
parameter estimates look like. We can subsequently customize the model.

## Compile Model
```{r compile}
#| eval: !expr params$refit

# Compile model
model <-
  cmdstanr::cmdstan_model(
    stan_file = here("src", "models", paste0(model_name, ".stan")),
    pedantic = TRUE,
    quiet = FALSE
  )
```

## Fit Model
```{r fit generic, eval=FALSE}
#| eval: !expr params$refit

# number of MCMC chains
n_chains <- 4
# Run sampler
fit <- model$sample(
  data = stan_data,
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 500,
  refresh = 500,
  thin = 1,
  adapt_delta = .8,
  init = .1
)

# save fit
fit$save_object(file =  here("fits", paste0(model_name, "quantifier_full_fit.RDS")))
```

```{r}
# load  fit
fit <- readRDS(file =  here("fits", paste0(model_name, "quantifier_full_fit.RDS")))
```

***

```{r}
parameters <- c(
  "Tr_loc",
  "Tr_wid",
  "E_loc",
  "E_wid",
  "a_loc",
  "b_loc",
  "lambda_loc",
  "lambda_wid",
  "omega",
  "mu_E",
  "sigma_I",
  "sigma_lambda",
  "rho_lambda",
  "rho_E",
  "rho_lambda"
)
```

```{r}
estimates_summary <- fit$summary(variables = parameters)
```

### Sampler Diagnostics

```{r}
# sampler diagnostics
fit$sampler_diagnostics(format = "df") %>% 
  psych::describe(quant = c(.05,.95),) %>%
  round(2) %>%  
  as.data.frame() %>% 
  dplyr::select(median, min, Q0.05, Q0.95,  max) %>% 
  .[-c(7:9),]
```

```{r}
# convergence diagnostics
convergence_summary <- 
  fit$draws(format = "df", variables = parameters) %>%
  summarise_draws(.x = ., "rhat", "ess_bulk", "ess_tail") %>%
  remove_missing() %>%
  select(-variable) %>%
  psych::describe(., quant = c(.05, .95)) %>%
  as.data.frame() %>%
  select(median, Q0.05, Q0.95, min, max)

convergence_summary %>% round(3)
```

### Effective sample size (ESS) & Rhat Plots
```{r}
# color scheme
color_scheme_set(scheme = "purple")

# Effective sample sizes
plot_neff <-
  mcmc_neff_hist(bayesplot::neff_ratio(fit, pars = parameters), binwidth = .01) +
  labs(title = "A") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  )
# Rhat
plot_rhat <-
  bayesplot::mcmc_rhat_hist(bayesplot::rhat(fit, pars = parameters)) +
  labs(title = "B") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  ) +
  yaxis_text(on = TRUE)

# Combined plot
plot_diagnostics <- gridExtra::grid.arrange(plot_neff, plot_rhat, ncol = 2)
```

## Parameter Plots
```{r}
# color scheme
color_scheme_set(scheme = "purple")
```

### Person Competence: Location
```{r }
# order estimates by size
E_loc_ordered <-
  fit$summary("E_loc") %>% 
  as.data.frame() %>% 
  arrange(median) %>% 
  select(variable) %>% 
  unlist()

# plot
mcmc_intervals(fit$draws(E_loc_ordered), point_est = "median", transformations = "log") +
  labs(
    subtitle = "Person Competence: Location",
    x = expression(E[loc]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Person Competence: Width
```{r }
# order estimates by size of theta
E_wid_ordered <- 
  str_replace(E_loc_ordered, "E_loc", "E_wid")

# plot
mcmc_intervals(fit$draws(E_wid_ordered), point_est = "median",transformations = "log") +
  labs(subtitle = "Person Competence: Width",
       x = expression(E[wid]),
       y = "Respondent") +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Correlation: Person Competence Location vs. Width
```{r fig.height = 2}
mcmc_intervals(fit$draws("rho_E"), point_est = "median") +
  bayesplot::vline_0(linetype = "dashed", color = "grey70") +
  labs(
    subtitle = "Correlation: Person Competence Location vs. Width",
    x = expression(rho[E]),
    y = "Respondent"
  ) +
  scale_x_continuous(limits = c(-1,1), expand = expansion()) +
  theme_itm(base_size = 16, hide_axis_text_y = TRUE) +
  theme(panel.grid = element_blank())
```

### Person Scaling Bias: Location
```{r }
# order estimates by size
a_loc_ordered <-
  fit$summary("a_loc") %>% 
  as.data.frame() %>% 
  arrange(median) %>% 
  select(variable) %>% 
  unlist()

# plot
  mcmc_intervals(fit$draws(a_loc_ordered), point_est = "median", transformations = "log") +
  labs(
    subtitle = "Person Scaling Bias: Location",
    x = expression(a[i]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16, hide_axis_text_y = TRUE) +
  theme(panel.grid = element_blank())
```

### Person Shifting Bias: Location
```{r }
# order estimates by size
b_loc_ordered <-
  fit$summary("b_loc") %>% 
  as.data.frame() %>% arrange(median) %>% 
  select(variable) %>% 
  unlist()

# plot
  mcmc_intervals(fit$draws(b_loc_ordered), point_est = "median") +
  labs(
    subtitle = "Person Shifting Bias: Location",
    x = expression(b_loc[i]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16, hide_axis_text_y = TRUE) +
  theme(panel.grid = element_blank())
```

We find no relevant variance for the person shifting bias. The model should 
therefore be simplfied by ommitting the person shifting bias.


### Person Shifting Bias: Width
```{r }
# order estimates by size of theta
b_wid_ordered <- 
  str_replace(b_loc_ordered, "b_loc", "b_wid")

# plot
mcmc_intervals(fit$draws(b_wid_ordered), point_est = "median") +
  labs(
    subtitle = "Person Shifting Bias: Width",
    x = expression(b_wid[i]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16, hide_axis_text_y = TRUE) +
  theme(panel.grid = element_blank())
```

### Item Discernability: Location
```{r }
mcmc_intervals(fit$draws("lambda_loc"), point_est = "median", transformations = "log") +
  labs(
    subtitle = "Item Discernability: Location",
    x = expression(lambda[loc]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Item Discernability: Width
```{r }
mcmc_intervals(fit$draws("lambda_wid"), point_est = "median",transformations = "log") +
  labs(
    subtitle = "Item Discernability: Width",
    x = expression(lambda[wid]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Correlation: Iem Discernibility, Location vs. Width
```{r fig.height=2}
mcmc_intervals(fit$draws("rho_lambda"), point_est = "median") +
  bayesplot::vline_0(linetype = "dashed", color = "grey70") +
  labs(x = expression(rho[lambda]), y = NULL) +
  scale_x_continuous(limits = c(-1, 1), expand = expansion()) +
  theme_itm(base_size = 16, hide_axis_text_y = TRUE) +
  theme(panel.grid = element_blank())
```

### Correlation of Residuals: Location vs. Width
```{r }
mcmc_intervals(fit$draws(c("omega")), point_est = "median") +
  
  labs(
    title = "B",
    subtitle = "DDRM: Expansion",
    x = expression(omega),
    y = "Respondent"
  ) +
  scale_x_continuous(limits = c(-1,1), expand = expansion()) +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Latent Consensus Intervals
```{r}
latent_truth <- data.frame(
  idx = 1:J,
  name = item_names_quantifier,
  lower = fit$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[1:J],
  wid = fit$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[(J +
                                                                             1):(J * 2)]
) %>%
  mutate(loc = lower + wid / 2, upper = lower + wid) %>%
  arrange(lower)

latent_truth %>% 
  ggplot(aes(x = loc, y = 1:J)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.3) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = seq(0, 1, .25),
    expand = expansion()
  ) +
  scale_y_continuous(breaks = 1:J, labels = item_names_quantifier[latent_truth$idx]) +
  labs(x = "Latent Truth",
       y = "Item") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank(), , axis.line.y = element_blank())

# save plot
ggsave(
  here("plots", "consensus_intervals_full_model.pdf"),
  width = 15,
  height = 8,
  units = "cm",
  scale = 1.4
)
```

```{r}
latent_truth %>% 
  mutate(across(c(lower, wid, loc, upper), ~round(., 3)*100)) %>% 
  select(-idx,-wid)
```


***

# Fit Customized Model

We removed the person shifting bias from the model.


### Compile Model  
Specify model name:
```{r}
# Choose model to fit
model_name_quantifier <- "itm_quantifier_beta"
```

```{r}
#| eval: !expr params$refit

# Compile model
model_quantifier <-
  cmdstanr::cmdstan_model(
    stan_file = here("src", "models", paste0(model_name_quantifier, ".stan")),
    pedantic = TRUE,
    quiet = TRUE
  )
```

### Fit Model 
```{r fit custom, eval=FALSE}
#| eval: !expr params$refit

# number of MCMC chains
n_chains <- 4

# Run sampler
fit_quantifier <- model_quantifier$sample(
  data = stan_data, 
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 500,
  thin = 1,
  init = .1,
  adapt_delta = .8
)
  
# save fit
fit_quantifier$save_object(file =  here("fits", paste0(model_name_quantifier, "_custom_fit.RDS")))
```

```{r load fit}
# load  fit
fit_quantifier <- readRDS(file =  here("fits", paste0(model_name_quantifier, "_custom_fit.RDS")))
```

```{r}
parameters <- parameters[parameters != "b_loc"]
```


### Summary
```{r}
estimates_summary_quantifier <- fit_quantifier$summary(parameters)
```

### Sampler Diagnostics
```{r}
# sampler diagnostics
fit_quantifier$sampler_diagnostics(format = "df") %>% 
  psych::describe(quant = c(.05,.95),) %>%
  round(2) %>%  
  as.data.frame() %>% 
  dplyr::select(median, min, Q0.05, Q0.95,  max) %>% 
  .[-c(7:9),]
```

```{r}
# convergence diagnostics
convergence_summary <- 
  fit_quantifier$draws(format = "df", variables = parameters) %>%
  summarise_draws(.x = ., "rhat", "ess_bulk", "ess_tail") %>%
  remove_missing() %>%
  select(-variable) %>%
  psych::describe(., quant = c(.05, .95)) %>%
  as.data.frame() %>%
  select(median, Q0.05, Q0.95, min, max)

convergence_summary %>% round(3)
```

### Effective sample size (ESS) & Rhat Plots
```{r}
# color scheme
color_scheme_set(scheme = "purple")

# Effective sample sizes
plot_neff <-
  mcmc_neff_hist(bayesplot::neff_ratio(fit_quantifier, pars = parameters),
                 binwidth = .01) +
  labs(title = "A") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  )
# Rhat
plot_rhat <-
  bayesplot::mcmc_rhat_hist(bayesplot::rhat(fit_quantifier, pars = parameters)) +
  labs(title = "B") +
  guides(color = FALSE, fill = FALSE) +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  ) +
  yaxis_text(on = TRUE)

# Combined plot
plot_diagnostics <- gridExtra::grid.arrange(plot_neff, plot_rhat, ncol = 2)
```

## Parameter Plots
```{r}
# color scheme
color_scheme_set(scheme = "purple")
```

### Person Competence: Location
```{r }
# order estimates by size
E_loc_ordered <-
  fit_quantifier$summary("E_loc") %>% 
  as.data.frame() %>% 
  arrange(median) %>% 
  select(variable) %>% 
  unlist()

# plot
  mcmc_intervals(fit_quantifier$draws(E_loc_ordered), point_est = "median", transformations = "log") +
  labs(
    subtitle = "Person Competence: Location",
    x = expression(log(E[i])),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Person Competence: Width
```{r }
# order estimates by size of theta
E_wid_ordered <- 
  str_replace(E_loc_ordered, "E_loc", "E_wid")

# plot

  mcmc_intervals(fit_quantifier$draws(E_wid_ordered), point_est = "median",transformations = "log") +
  labs(subtitle = "Person Competence: Width",
       x = expression(log(E_wid[i])),
       y = "Respondent") +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Correlation: Person Competence Location vs. Width
```{r fig.height = 2}
mcmc_intervals(fit_quantifier$draws("rho_E"), point_est = "median") +
  labs(
    title = "B",
    subtitle = "Correlation: Person Competence Location vs. Width",
    x = expression(Omega[i]),
    y = "Respondent"
  ) +
  xlim(-1,1)  +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

```{r}
fit_quantifier$draws("rho_E") %>% 
  bayestestR::describe_posterior(ci_method = "hdi")
```

### Person Scaling Bias: Location
```{r }
# order estimates by size
a_loc_ordered <-
  fit_quantifier$summary("a_loc") %>% 
  as.data.frame() %>% arrange(median) %>% 
  select(variable) %>% 
  unlist()

# plot
mcmc_intervals(fit_quantifier$draws(a_loc_ordered), point_est = "median", transformations = "log") +
  labs(
    subtitle = "Person Scaling Bias: Location",
    x = expression(log(a[i])),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Person Shifting Bias: Width
```{r }
mcmc_intervals(fit_quantifier$draws("b_wid"), point_est = "median") +
  labs(
    subtitle = "Person Shifting Bias: Width",
    x = expression(b_wid[i]),
    y = "Respondent"
  ) +
  scale_y_discrete(labels = NULL, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Item Discernability: Location
```{r }
 mcmc_intervals(fit_quantifier$draws("lambda_loc"), point_est = "median", transformations = "log") +
  labs(
    subtitle = "Item Discernability: Location",
    x = expression(log(lambda[loc])),
    y = "Item"
  ) +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02))  +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Item Discernability: Width
```{r }
mcmc_intervals(fit_quantifier$draws("lambda_wid"), point_est = "median",transformations = "log") +
  labs(
    subtitle = "Item Discernability: Width",
    x = expression(log(lambda[wid])),
    y = "Item"
  ) +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Correlation: Item Discernibility Location vs. Width
```{r fig.height=2}
mcmc_intervals(fit_quantifier$draws("rho_lambda"), point_est = "median") +
  labs(
    x = expression(Omega[j])
  ) +
  xlim(-1,1) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```


```{r}
fit_quantifier$draws("rho_lambda") %>% 
  bayestestR::describe_posterior(ci_method = "hdi")
```


### Correlation Between Location and Width
```{r }
  mcmc_intervals(fit_quantifier$draws(c("omega")), point_est = "median") +
  labs(
    subtitle = "Residual Correlation",
    x = expression(omega[j]),
    y = "Item"
  ) +
  scale_x_continuous(limits = c(-1,1)) +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Latent Truth Intervals
```{r}
latent_truth <- data.frame(
  idx = 1:J,
  name = item_names_quantifier,
  lower_consensus = fit_quantifier$summary("Tr_splx") %>%
    as.data.frame() %>%
    pull(median) %>%
    .[1:J],
  wid_consensus = fit_quantifier$summary("Tr_splx") %>%
    as.data.frame() %>%
    pull(median) %>%
    .[(J + 1):(J * 2)]
) %>%
  mutate(
    loc_consensus = lower_consensus + wid_consensus / 2,
    upper_consensus = lower_consensus + wid_consensus
  ) %>%
  arrange(lower_consensus)

latent_truth %>%
  # plot
  ggplot(aes(x = loc_consensus, y = 1:J)) +
  geom_errorbarh(aes(xmin = lower_consensus, xmax = upper_consensus), height = 0.3) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = seq(0, 1, .25),
    expand = expansion()
  ) +
  scale_y_continuous(breaks = 1:J, labels = item_names_quantifier[latent_truth$idx]) +
  labs(x = "Latent Truth", y = "Item") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank(), axis.line.y = element_blank())

# save plot
ggsave(
  here("plots", "consensus_intervals_custom_model.pdf"),
  width = 15,
  height = 8,
  units = "cm",
  scale = 1.4
)
```

```{r}
latent_truth %>% 
  mutate(across(c(lower_consensus, wid_consensus, loc_consensus, upper_consensus), ~round(., 3)*100)) %>% 
  select(-idx,-wid_consensus)
```


***

# Density Plots

### Prepare Data
```{r}
df_long <- df_long %>%
  group_by(jj) %>%
  mutate(
    loc_mean = mean((x_L + x_U) / 2, na.rm = TRUE),
    wid_mean = mean(x_U - x_L, na.rm = TRUE),
    lower_mean = loc_mean - wid_mean / 2,
    upper_mean = loc_mean + wid_mean / 2,
    loc_mean_logit = mean(x_bvn_1, na.rm = TRUE),
    wid_mean_logit = mean(x_bvn_2, na.rm = TRUE)
  ) %>%
  ungroup()

splx <- bvn_to_simplex(df_long[, c("loc_mean_logit", "wid_mean_logit")])
df_long$lower_mean_logit <- splx[, 1]
df_long$upper_mean_logit <- 1 - splx[, 3]
```

### Plot: Verbal Quantifiers All
```{r fig.height=15}
df <- df_long %>%
  select(jj,
         name_en,
         x_L,
         x_U,
         lower_mean,
         upper_mean,
         lower_mean_logit,
         upper_mean_logit,
         truth) %>%
  remove_missing(vars = c("x_L", "x_U")) %>%
  full_join(., latent_truth, by = c("jj" = "idx"))

plot_density <-
  plot_intvls_aggregated(
    lower = df$x_L,
    upper = df$x_U,
    item_id = as.double(df$jj),
    lower_mean = df$lower_consensus * 100,
    upper_mean = df$upper_consensus * 100,
    lower_mean_logit = df$lower_mean_logit * 100,
    upper_mean_logit = df$upper_mean_logit * 100,
    item_name = df$name_en,
    facet_wrap = TRUE,
    min = 0,
    max = 100,
    step_size = 1,
    show_quantiles = FALSE
  )

plot_density

# save plot
ggsave(
  plot = plot_density,
  here("plots", "verbal_quantifier_densities_all.pdf"),
  width = 15,
  height = 15,
  units = "cm",
  scale = 1.7
)
```

### Plot: Verbal Quantifiers Selection for Article
```{r}
df <- df_long %>%
  select(
    jj,
    name_en,
    x_L,
    x_U,
    lower_mean,
    upper_mean,
    lower_mean_logit,
    upper_mean_logit,
    truth
  ) %>%
  dplyr::filter(name_en %in% c("fifty-fifty chance", "hardly", "potentially")) %>%
  full_join(., latent_truth, by = c("jj" = "idx")) %>%
  remove_missing(vars = c("x_L", "x_U"))


# Layout for facet wrap
design <- matrix(c(1, 2, 1, 3), 2, 2)
# plot
plot_selection <-
  plot_intvls_aggregated(
    lower = df$x_L,
    upper = df$x_U,
    item_id = as.double(df$jj),
    lower_mean = df$lower_consensus * 100,
    upper_mean = df$upper_consensus * 100,
    lower_mean_logit = df$lower_mean_logit * 100,
    upper_mean_logit = df$upper_mean_logit * 100,
    item_name = (df$name_en),
    truth = df$truth,
    facet_wrap = TRUE,
    design = design,
    ncol = 2,
    min = 0,
    max = 100,
    step_size = 1,
    show_quantiles = FALSE
  )
plot_selection

# save plot
ggsave(
  plot = plot_selection,
  here("plots", "verbal_quantifier_densities_example.pdf"),
  width = 15,
  height = 7.5,
  units = "cm",
  scale = 1.6
)
```


```{r}
### Plot for slides

df <- df_long %>%
    select(
    jj,
    name_en,
    x_L,
    x_U,
    lower_mean,
    upper_mean,
    lower_mean_logit,
    upper_mean_logit,
    truth
  ) %>%
  dplyr::filter(name_en %in% c("fifty-fifty chance")) %>%
  full_join(., latent_truth, by = c("jj" = "idx")) %>%
  remove_missing(vars = c("x_L", "x_U")) 


# plot
plot_selection <-  plot_intvls_aggregated(
  lower = df$x_L,
  upper = df$x_U,
  item_id = as.double(df$jj),
  lower_mean = df$lower_consensus*100,
  upper_mean = df$upper_consensus*100,
  lower_mean_logit = df$lower_mean_logit*100,
  upper_mean_logit = df$upper_mean_logit*100,
  item_name = (df$name_en),
  truth = df$truth,
  facet_wrap = FALSE,
  ncol = 2,
  min = 0,
  max = 100,
  step_size = 1,
  show_quantiles = FALSE
)
#plot_selection

# save plot
ggsave(
  plot = plot_selection,
  here("plots", "verbal_quantifier_densities_50-50.pdf"),
  width = 15,
  height = 5,
  units = "cm",
  scale = 1.6
)

ggsave(
  plot = plot_selection,
  here("plots", "verbal_quantifier_densities_50-50.svg"),
  width = 15,
  height = 5,
  units = "cm",
  scale = 1.6
)
```

```{r}
### Plot for slides
df <- df_long %>%
  select(
    jj,
    name,
    name_en,
    x_L,
    x_U,
    lower_mean,
    upper_mean,
    lower_mean_logit,
    upper_mean_logit,
    truth
  ) %>%
  dplyr::filter(name %in% c("meistens")) %>%
  full_join(., latent_truth, by = c("jj" = "idx")) %>%
  remove_missing(vars = c("x_L", "x_U")) 


# plot
plot_selection <-  plot_intvls_aggregated(
  lower = df$x_L,
  upper = df$x_U,
  item_id = as.double(df$jj),
  lower_mean = df$lower_consensus*100,
  upper_mean = df$upper_consensus*100,
  lower_mean_logit = df$lower_mean_logit*100,
  upper_mean_logit = df$upper_mean_logit*100,
  item_name = (df$name_en),
  truth = df$truth,
  facet_wrap = FALSE,
  ncol = 2,
  min = 0,
  max = 100,
  step_size = 1,
  show_quantiles = FALSE
)
#plot_selection

# save plot
ggsave(
  plot = plot_selection,
  here("plots", "verbal_quantifier_densities_mostly.pdf"),
  width = 15,
  height = 5,
  units = "cm",
  scale = 1.6
)

ggsave(
  plot = plot_selection,
  here("plots", "verbal_quantifier_densities_mostly.svg"),
  width = 15,
  height = 5,
  units = "cm",
  scale = 1.6
)
```


## Responses vs. Proficiency

```{r}
# prepare data
proficiency_loc <- 
  fit_quantifier$summary("E_loc") %>% as.data.frame() %>% select(median) %>% 
  rename(proficiency_loc = median) %>%
  mutate(ii = 1:I,
         proficiency_loc = scale(log(proficiency_loc)))

proficiency_wid <- 
  fit_quantifier$summary("E_wid") %>% as.data.frame() %>% select(median) %>%
  rename(proficiency_wid = median) %>%
  mutate(ii = 1:I,
         proficiency_wid = scale(log(proficiency_wid))) 

proficiency_medians <-
  full_join(proficiency_loc, proficiency_wid, by = c("ii" = "ii")) %>%
  full_join(., df_long %>%
              select(ii, x_L_u, x_U_u, name), by = c("ii" = "ii")) %>%
  mutate(
    proficiency = (proficiency_loc + proficiency_wid) / 2,
    ii_ranked = factor(proficiency) %>% as.numeric()
  ) %>%
  arrange(proficiency) %>%
  dplyr::filter(name == "Fuenfzig-Fuenfzig Chance")


# plot
plot_proficiency_vs_intervals <- 
  proficiency_medians %>%
  ggplot() +
  geom_rect(aes(
    xmin = 40,
    xmax = 60,
    ymin = 0,
    ymax = max(ii_ranked) + 1
  ), color = "grey80") +
  geom_errorbar(aes(
    y = (ii_ranked),
    xmin = x_L_u,
    xmax = x_U_u
  ),  
  alpha = .5,
  width = 2,
  linewidth = .5) +
  geom_point(
    aes(x = pnorm(proficiency), y = ii_ranked), 
    shape = 16,
    col = ggokabeito::palette_okabe_ito()[5]
    ) +
  scale_x_continuous(
    limits = c(0, 1),
    breaks = seq(0, 1, .25),
    labels = c("0", ".25", ".50", ".75", "1"),
    expand = expansion()
  ) +
  scale_y_continuous(expand = expansion(0, .2)) +
  labs(
    x = "Response Interval / <span style='color: #0072B2;'>Transformed Proficiency</span>", 
    y = "Respondent") +
  coord_cartesian(clip = "off") +
  theme_itm() +
  theme(
    axis.title.x = ggtext::element_markdown(),
    axis.line = element_line(colour = "#6d6d6e", size = .3),
    axis.ticks.x = element_line(colour = "#6d6d6e", size = .3),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid = ggplot2::element_blank(
    )
  )

ggsave(
  plot = plot_proficiency_vs_intervals,
  filename = here("plots", "proficiency_vs_intervals.pdf"),
  width = 15,
  height = 10,
  units = "cm",
  scale = 1.4
)

plot_proficiency_vs_intervals
```

# Prior vs. Posterior
## True Intervals
```{r}
latent_truth <- data.frame(
  Tr_loc_splx_post = fit_quantifier$draws("Tr_loc_splx") %>%
    unlist() %>%
    as.vector(),
  Tr_wid_splx_post = fit_quantifier$draws("Tr_wid_splx") %>%
    unlist() %>%
    as.vector()
) %>%
  mutate(
    jj = factor(rep(1:J, each = nrow(.) / J)),
    Tr_wid_splx_prior = rbeta(nrow(.), 1.2, 3),
    Tr_loc_splx_prior = (1 - Tr_wid_splx_prior) * rbeta(nrow(.), 1, 1) + Tr_wid_splx_prior / 2
  )

Tr_bvn <- simplex_to_bvn(
  cbind(
    latent_truth$Tr_loc_splx_prior - .5 * latent_truth$Tr_wid_splx_prior,
    latent_truth$Tr_wid_splx_prior,
    1 - (
      latent_truth$Tr_loc_splx_prior + .5 * latent_truth$Tr_wid_splx_prior
    )
  )
)
latent_truth <- cbind(latent_truth,
                      Tr_loc_prior = Tr_bvn[, 1], Tr_wid_prior = Tr_bvn[, 2])


latent_truth %>%
  ggplot() +
  geom_abline(intercept = 0,
              slope = 2,
              alpha = .7) +
  geom_abline(intercept = 2,
              slope = -2,
              alpha = .7) +
  geom_density_2d_filled(
    aes(x = Tr_loc_splx_prior, 
        y = Tr_wid_splx_prior), 
    alpha = .3, 
    binwidth = .05
    ) +
  geom_point(
    aes(x = Tr_loc_splx_post, y = Tr_wid_splx_post, col = jj),
    size = .3,
    alpha = .3,
    shape = 16
  ) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = c("0", ".25", ".5", ".75", "1"),
    expand = expansion()
  ) +
  labs(x = "Location", y = "Width") +
  # supress legends
  guides(col = FALSE, fill = FALSE) +
  theme_pubr()
```


## Hyper-Priors
### sigma_lambda: Location
```{r}
sigma_lambda_loc <- data.frame(posterior = fit_quantifier$draws("sigma_lambda[1]", format = "list") %>% unlist() %>%  as.vector())
sigma_lambda_loc$prior <- exp(rnorm(nrow(sigma_lambda_loc), log(.5), .5))

sigma_lambda_loc %>%
  ggplot() +
  geom_density(aes(prior), fill = "lightblue", alpha = 1) +
  geom_density(aes(exp(posterior * .5 + log(.5))), fill = "purple", alpha = .3) +
  scale_x_continuous(limits = c(NA, 3), expand = expansion()) +
  scale_y_continuous(limits = c(0, NA), expand = expansion()) +
  labs(x = "Prior / Posterior", y = "Density")  +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### sigma_lambda: Width
```{r}
sigma_lambda_wid <- data.frame(
  posterior = fit_quantifier$draws("sigma_lambda[2]", format = "list") %>% unlist() %>%  as.vector()
)
sigma_lambda_wid$prior <- exp(rnorm(nrow(sigma_lambda_loc), log(.5), .5))

sigma_lambda_wid %>% 
  ggplot() +
  geom_density(
    aes(prior),
    fill = "lightblue",
    alpha = 1  ) +
  geom_density(aes(exp(posterior*.5+log(.5))),
               fill = "purple",
               alpha = .3
               ) +
  scale_x_continuous(
    limits = c(NA, 3),
    expand = expansion()
  ) +
  scale_y_continuous(limits = c(0, NA), expand = expansion()) +
  labs(x = "Prior / Posterior", y = "Density") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### sigma_E: Location
```{r}
sigma_E_loc <- data.frame(
  posterior = fit_quantifier$draws("sigma_I[1]", format = "list") %>% unlist() %>%  as.vector()
)
sigma_E_loc$prior <- exp(rnorm(nrow(sigma_lambda_loc), log(.5), .5))

sigma_E_loc %>% 
  ggplot() +
  geom_density(
    aes(prior),
    fill = "lightblue",
    alpha = 1  ) +
  geom_density(aes(exp(posterior*.5+log(.5))),
               fill = "purple",
               alpha = .3
               ) +
  scale_x_continuous(
    limits = c(NA, 3),
    expand = expansion()
  ) +
  scale_y_continuous(limits = c(0, NA), expand = expansion()) +
  labs(x = "Prior / Posterior", y = "Density") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### sigma_E: Width
```{r}
sigma_E_wid <- data.frame(
  posterior = fit_quantifier$draws("sigma_I[2]", format = "list") %>% unlist() %>%  as.vector()
)
sigma_E_wid$prior <- exp(rnorm(nrow(sigma_lambda_loc), log(.5), .5))

sigma_E_wid %>% 
  ggplot() +
  geom_density(
    aes(prior),
    fill = "lightblue",
    alpha = 1  ) +
  geom_density(aes(exp(posterior*.5+log(.5))),
               fill = "purple",
               alpha = .3
               ) +
  scale_x_continuous(
    limits = c(NA, 3),
    expand = expansion()
  ) +
  scale_y_continuous(limits = c(0, NA), expand = expansion()) +
  labs(x = "Prior / Posterior", y = "Density") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### mu_E: Location
```{r}
mu_E_loc <- data.frame(
  posterior = fit_quantifier$draws("mu_E[1]", format = "list") %>% unlist() %>%  as.vector()
)
mu_E_loc$prior <- rnorm(nrow(sigma_lambda_loc))

mu_E_loc %>% 
  ggplot() +
  geom_density(
    aes(prior),
    fill = "lightblue",
    alpha = 1  ) +
  geom_density(aes(posterior),
               fill = "purple",
               alpha = .3
               ) +
  scale_x_continuous(
    limits = c(-4, 4),
    expand = expansion()
  ) +
  scale_y_continuous(limits = c(0, NA), expand = expansion()) +
  labs(x = "Prior / Posterior", y = "Density") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### mu_E: Width
```{r}
mu_E_wid <- data.frame(
  posterior = fit_quantifier$draws("mu_E[2]", format = "list") %>% unlist() %>%  as.vector()
)
mu_E_wid$prior <-  rnorm(nrow(sigma_lambda_loc))

mu_E_wid %>% 
  ggplot() +
  geom_density(
    aes(prior),
    fill = "lightblue",
    alpha = 1  ) +
  geom_density(aes(posterior),
               fill = "purple",
               alpha = .3
               ) +
  scale_x_continuous(
    limits = c(-4, 4),
    expand = expansion()
  ) +
  scale_y_continuous(limits = c(0, NA), expand = expansion()) +
  labs(x = "Prior / Posterior", y = "Density") +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```



# Posterior Predictive Checks
```{r}
sample <- sample(1:1000, 100)
Y_ppc_loc <- fit_quantifier$draws("Y_ppc_loc", format = "matrix")[sample,]
Y_ppc_wid <- fit_quantifier$draws("Y_ppc_wid", format = "matrix")[sample,]
Y_ppc_loc_splx <- fit_quantifier$draws("Y_ppc_loc_splx", format = "matrix")[sample,]
Y_ppc_wid_splx <- fit_quantifier$draws("Y_ppc_wid_splx", format = "matrix")[sample,]
```

### Location: Bivariate Normal
```{r}
bayesplot::ppc_dens_overlay(y = df_long$x_bvn_1, yrep = Y_ppc_loc) +
  xlim(-10, 10)
```

### Width: Bivariate Normal
```{r}
bayesplot::ppc_dens_overlay(
  y = df_long$x_bvn_2,
  yrep = Y_ppc_wid
  ) +
  xlim(-10,10) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Location: Bounded
```{r}
bayesplot::ppc_dens_overlay(y = df_long$x_M_u, yrep = Y_ppc_loc_splx) +
  xlim(0, 1)
```

### Width: Bounded
```{r}
bayesplot::ppc_dens_overlay(y = df_long$x_W_u, yrep = Y_ppc_wid_splx) +
  xlim(0, 1) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Lower Interval Bound
```{r}
bayesplot::ppc_dens_overlay(y = df_long$x_L_u, yrep = Y_ppc_loc_splx - Y_ppc_wid_splx/2) +
  xlim(0, 1)
```

### Upper Interval Bound
```{r}
bayesplot::ppc_dens_overlay(y = df_long$x_U_u, yrep = Y_ppc_loc_splx + Y_ppc_wid_splx/2) +
  xlim(0, 1) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```


# Re-Fit Without Control Items

## Stan Data
```{r}
### Stan data declaration
df_long_no_controls <- 
  df_long %>% 
  dplyr::filter(!name %in% c("Fuenfzig-Fuenfzig Chance", "immer", "niemals")) %>% 
  mutate(
    ii = as.integer(as.factor(ii)),
    jj = as.integer(as.factor(jj))
  )

## stan data list
stan_data_no_controls <- list(
  I = length(unique(df_long_no_controls$ii)),
  J = length(unique(df_long_no_controls$jj)),
  N = nrow(df_long_no_controls),
  ii =  df_long_no_controls$ii,
  jj = df_long_no_controls$jj,
  nn = c(1:nrow(df_long_no_controls)),
  Y_splx = cbind(
    df_long_no_controls$x_splx_1,
    df_long_no_controls$x_splx_2,
    df_long_no_controls$x_splx_3
  ) %>%
    as.matrix()
)
```

### Fit Model 
```{r fit no controls, eval=FALSE}
#| eval: !expr params$refit

# number of MCMC chains
n_chains <- 4

# Run sampler
fit_quantifier_no_controls <- model_quantifier$sample(
  data = stan_data_no_controls, 
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 500,
  thin = 1,
  init = .1,
  adapt_delta = .8
)
  
# save fit
fit_quantifier_no_controls$save_object(file =  here("fits", paste0(model_name_quantifier, "_no_controls_fit.RDS")))
```

```{r}
# load  fit
fit_quantifier_no_controls <- readRDS(file =  here("fits", paste0(model_name_quantifier, "_no_controls_fit.RDS")))
```

### Item Discernability: Location
```{r }
mcmc_intervals(
  fit_quantifier_no_controls$draws("lambda_loc"),
  point_est = "median",
  transformations = "log"
) +
  labs(subtitle = "Item Discernability: Location",
       x = expression(log(lambda[loc])),
       y = "Item") +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

### Item Discernability: Width
```{r }
mcmc_intervals(
  fit_quantifier_no_controls$draws("lambda_wid"),
  point_est = "median",
  transformations = "log"
) +
  labs(subtitle = "Item Discernability: Width",
       x = expression(log(lambda[wid])),
       y = "Item") +
  scale_y_discrete(labels = item_names_quantifier, expand = expansion(.02)) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

## Discernibility: Correlation Between Location and Width
```{r fig.height=2}
mcmc_intervals(fit_quantifier_no_controls$draws("rho_lambda"), point_est = "median") +
  labs(
    x = expression(Omega[j])
  ) +
  xlim(-1,1) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

```{r}
fit_quantifier_no_controls$draws("rho_lambda") %>% 
  bayestestR::describe_posterior(ci_method = "hdi")
```


## Proficiency: Correlation Between Location and Width
```{r fig.height=2}
mcmc_intervals(fit_quantifier_no_controls$draws("rho_E"), point_est = "median") +
  labs(
    x = expression(Omega[j])
  ) +
  xlim(-1,1) +
  theme_itm(base_size = 16) +
  theme(panel.grid = element_blank())
```

```{r}
fit_quantifier_no_controls$draws("rho_E") %>% 
  bayestestR::describe_posterior(ci_method = "hdi")
```

# Session Info
```{r}
sessionInfo()
```