---
title: "Interval Consensus Model"
subtitle: "Sensitivity Analyses for Zero Handling Methods"
author: 
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-format: "png"
    fig-width: 7
    fig-height: 7
    fig-responsive: true
    embed-resources: true
execute:
  message: false
  warning: false
params: 
  refit: false
---

```{r setup}
# Libraries
packages <- c(
  "tidyverse",
  "rmarkdown",
  "svglite",
  "psych",
  "here",
  "ggpubr",
  "gridExtra",
  "extraDistr"
)
# in case cmdstanr is not installed
# install.packages("cmdstanr",
#                  repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

if (!require("pacman"))
  install.packages("pacman")
pacman::p_load(packages, update = F, character.only = T)

# default chunk options
knitr::opts_chunk$set(
  # fig.height = 7,
  # fig.width = 10,
  include = TRUE,
  message = FALSE,
  warning = FALSE
)
source(here("src", "00_functions.R"))
set.seed(35032)
```

# Illustration of Zero-Handling Methods

## Uniform Reference Distribution for Comparison

```{r}
distribution <- extraDistr::rdirichlet(1e4, c(1,1,1)) |> 
  simplex_to_bvn()

mean_1 <- mean(distribution$x_bvn_1)
sd_1 <- sd(distribution$x_bvn_1)

mean_2 <- mean(distribution$x_bvn_2)
sd_2 <- sd(distribution$x_bvn_2)
```

Mean of the unbounded location:
```{r}
mean_1
```

Standard deviation of the unbounded location:
```{r}
sd_1
```

Mean of the unbounded width:
```{r}
mean_2
```

Standard deviation of the unbounded width:
```{r}
sd_2
```


## Define Edge Cases with Zeros and Padding Constants
```{r}
# edge_cases_raw <- rbind(
#   "[0,1]" = c(0,1,0),
#   "[0,.5]" = c(0,.5,.5),
#   "[0,0]" = c(0,0,1),
#   "[.5,.5]" = c(.5,0,.5)
# )

edge_cases_raw <- rbind(
  "A" = c(0,1,0),
  "B" = c(0,.5,.5),
  "C" = c(0,0,1),
  "D" = c(.5,0,.5)
)

rownames(edge_cases_raw)

padding <- list(.02, .01, .005, .001)
levels <- c(.001, .005, .01, .02)
labels <- c("0.1%", "0.5%", "1%", "2%")
```

Also load empirical data for reference and later model sensitivity ckecks
```{r}
# Load empirical data for edge cases analysis
if (!file.exists(here("data", "df_master_long.rds"))) {
  osf_retrieve_file("https://osf.io/7azbr") |>
    osf_download(path = here("data"))
}

# Load and process empirical data
df_long <- read_rds(here("data", "df_master_long.rds")) |>
  dplyr::filter(domain == "prob_phrase") |> 
  # recompute indices
  mutate(jj = as.integer(factor(jj)),
         ii = as.integer(factor(ii)))

df_long$name_en[df_long$name_en == "Fifty-fifty chance"] <- "fifty-fifty chance"

empirical_raw <- df_long |> 
  mutate(
    x_1 = x_L / 100,
    x_2 = (x_U - x_L) / 100,
    x_3 = 1 - x_U / 100
    ) |> 
  select(x_1, x_2, x_3) |>
  remove_missing()
```


## Define Replacement Methods

### Additive Replacement
```{r}
additive_replacement <- function(simplex, padding = .01) {
  if (is.vector(simplex)) {
    simplex <- t(as.matrix(simplex))
  }
  
  if (is.data.frame(simplex)) {
    simplex <- as.matrix(simplex)
  }
  
  replace <- function(x, padding) {
    n_zeros <- sum(x == 0)
    
    x_new <- x
    
    x_new[x == 0] <- (padding * (n_zeros + 1) * (3 - n_zeros)) / 9
    x_new[x != 0] <- x[x != 0] - (padding * (n_zeros + 1) * n_zeros) / 9
    
    return(x_new)
  }
  
  simplex <- apply(X = simplex, MARGIN = 1, FUN = replace, padding) |> t()

  
  return(simplex)
}

additive_replacement(edge_cases_raw, padding = .01) |>
        as.data.frame() |> simplex_to_bvn()
```

### Simple Replacement
```{r}
simple_replacement <- function(simplex, padding = .01) {
  if (is.vector(simplex)) {
    simplex <- t(as.matrix(simplex))
  }
  
  if (is.data.frame(simplex)) {
    simplex <- as.matrix(simplex)
  }
  
  replace <- function(x, padding) {
    n_zeros <- sum(x == 0)
    x_new <- x
    x_new[x == 0] <- padding / (1 + n_zeros * padding)
    x_new[x != 0] <- x[x != 0] / (1 + n_zeros * padding)
    
    return(x_new)
  }
  
  simplex <- apply(X = simplex,
                   MARGIN = 1,
                   FUN = replace,
                   padding) |> t()
  
  return(simplex)
}

simple_replacement(edge_cases_raw, padding = .01)

simple_replacement(edge_cases_raw, padding = .01) |>
  as.data.frame() |> simplex_to_bvn()
```


### Multiplicative Replacement
```{r}
multiplicative_replacement <- function(simplex, padding = .01) {
  if (is.vector(simplex)) {
    simplex <- t(as.matrix(simplex))
  }
  
  if (is.data.frame(simplex)) {
    simplex <- as.matrix(simplex)
  }
  
  replace <- function(x, padding) {
    n_zeros <- sum(x == 0)
    
    x_new <- x
    
    x_new[x == 0] <- padding
    x_new[x != 0] <- x[x != 0] * (1 - padding * n_zeros)
    
    return(x_new)
  }
  
  simplex <- apply(X = simplex, MARGIN = 1, FUN = replace, padding) |> t()
  
  return(simplex)
}

multiplicative_replacement(edge_cases_raw, padding = .01)
multiplicative_replacement(edge_cases_raw, padding = .01) |>
        as.data.frame() |> simplex_to_bvn()
```

### Rescaling Replacement
```{r}
rescaling_replacement <- function(simplex, padding = .01) {
  if (is.vector(simplex)) {
    simplex <- t(as.matrix(simplex))
  }
  
  if (is.data.frame(simplex)) {
    simplex <- as.matrix(simplex)
  }
  
  # simple replacement
  simplex <- (simplex + padding)
  simplex <- simplex / (1 + padding * 3)
  
  return(simplex)
}

rescaling_replacement(edge_cases_raw, padding = .01)
rescaling_replacement(edge_cases_raw, padding = .01) |>
        as.data.frame() |> simplex_to_bvn()
```

## Plots

### Additive
```{r}
# Edge Cases
edge_cases_bvn_additive <-
  lapply(padding, FUN = function(X) {
    edge_cases_padded <- additive_replacement(edge_cases_raw, padding = X) |>
      as.data.frame()
    
    edge_cases_padded_bvn <- simplex_to_bvn(edge_cases_padded)
    edge_cases_padded_bvn$p_1 <- pnorm(edge_cases_padded_bvn$x_bvn_1, mean_1, sd_1) |> round(5)
    edge_cases_padded_bvn$p_2 <- pnorm(edge_cases_padded_bvn$x_bvn_2, mean_2, sd_2) |> round(5)
    edge_cases_padded_bvn$padding <- X
    edge_cases_padded_bvn$item <- rownames(edge_cases_raw)
    edge_cases_padded_bvn$method <- "additive"
    
    return(edge_cases_padded_bvn)
  })

edge_cases_bvn_additive <- do.call(what = "rbind", edge_cases_bvn_additive) |>
  mutate(item = factor(item),
         padding = factor(
           padding,
           levels = levels,
           labels = labels
         ))

# Empirical Data
empirical_bvn_additive <-
  lapply(padding, FUN = function(X) {
    empirical_padded <- additive_replacement(empirical_raw |> select(x_1, x_2, x_3), padding = X) |>
      as.data.frame()

    empirical_padded_bvn <- simplex_to_bvn(empirical_padded)
    empirical_padded_bvn$p_1 <- pnorm(empirical_padded_bvn$x_bvn_1, mean_1, sd_1) |> round(5)
    empirical_padded_bvn$p_2 <- pnorm(empirical_padded_bvn$x_bvn_2, mean_2, sd_2) |> round(5)
    empirical_padded_bvn$padding <- X
    empirical_padded_bvn$method <- "additive"

    return(empirical_padded_bvn)
  })

empirical_bvn_additive <- do.call(what = "rbind", empirical_bvn_additive) |>
  mutate(
         padding = factor(
           padding,
           levels = levels,
           labels = labels
         ))
```

```{r}
# plotting function
plot_edge_cases <- function(distribution, edge_cases_bvn, title) {
  plot <-
    ggplot() +
    geom_vline(xintercept = 0,
               linetype = 2,
               alpha = .2) +
    geom_hline(yintercept = 0,
               linetype = 2,
               alpha = .2) +
    geom_point(
      data = distribution,
      aes(x_bvn_1, x_bvn_2),
      alpha = .1,
      size = .1
    ) +
    # geom_point(
    #   data = edge_cases_bvn,
    #   aes(x = x_bvn_1, y = x_bvn_2),
    #   
    #   size = 3,
    #   color = "#d95f02"
    # ) +
    geom_label(
      data = edge_cases_bvn,
      aes(
        x = x_bvn_1,
        y = x_bvn_2,
        label = factor(item)
      ),
      family = "sans",
      face = "bold",
      size.unit = "pt",
      size = 12,
      #nudge_y = .95,
      label.size = 0,
      alpha = .7,
      label.padding = unit(0.2, "lines"),
      color = "#d95f02"
    ) +
    scale_x_continuous(
      limits = c(-6.7, 5),
      breaks = seq(-4, 4, 2),
      expand = expansion(0, 0)
    ) +
    scale_y_continuous(
      limits = c(-6.2, 7),
      breaks = seq(-4, 4, 2),
      expand = expansion(0, 0)
    ) +
    coord_equal() +
    labs(
      x = "Unbounded Location",
      y = "Unbounded Width",
      title = title,
      subtitle = "A: [0,1], B: [0,.5], C: [0,0], D: [.5,.5]"
    ) +
    facet_wrap(vars(padding)) +
    theme_icm() +
    theme(
      strip.text = element_text(
        face = "plain",
        size = ggplot2::rel(1),
        hjust = 0.5
      ),
      panel.grid = element_blank(),
      axis.line = element_line(colour = "#6d6d6e", size = .3),
      axis.ticks = element_line(colour = "#6d6d6e", size = .3),
      axis.title.y = element_text(margin = margin(0, -5, 0, 0, "pt"))
    )
  return(plot)
}
```

### Edge Cases With Reference Distribution
```{r}
plot_additive_replacement <- plot_edge_cases(
  distribution,
  edge_cases_bvn_additive,
  title = "Additive Replacement"
)

plot_additive_replacement
```

#### Edge Cases With Empirical Data
```{r}
plot_additive_replacement <- plot_edge_cases(
  distribution = empirical_bvn_additive,
  edge_cases_bvn = edge_cases_bvn_additive,
  title = "Additive Replacement"
)

plot_additive_replacement
```


#### Simple
```{r}
# Edge Cases
edge_cases_bvn_simple <-
  lapply(padding, FUN = function(X) {
    edge_cases_padded <- simple_replacement(edge_cases_raw, padding = X) |>
      as.data.frame()
    
    edge_cases_padded_bvn <- simplex_to_bvn(edge_cases_padded)
    edge_cases_padded_bvn$p_1 <- pnorm(edge_cases_padded_bvn$x_bvn_1, mean_1, sd_1) |> round(5)
    edge_cases_padded_bvn$p_2 <- pnorm(edge_cases_padded_bvn$x_bvn_2, mean_2, sd_2) |> round(5)
    edge_cases_padded_bvn$padding <- X
    edge_cases_padded_bvn$item <- rownames(edge_cases_raw) 
    edge_cases_padded_bvn$method <- "simple"
    
    return(edge_cases_padded_bvn)
  })

edge_cases_bvn_simple <- do.call(what = "rbind", edge_cases_bvn_simple) |>
  mutate(item = factor(item),
         padding = factor(
           padding,
           levels = levels,
           labels = labels
         ))

# Empirical Data
empirical_bvn_simple <-
  lapply(padding, FUN = function(X) {
    empirical_padded <- simple_replacement(empirical_raw, padding = X) |>
      as.data.frame()
    
    empirical_padded_bvn <- simplex_to_bvn(empirical_padded)
    empirical_padded_bvn$p_1 <- pnorm(empirical_padded_bvn$x_bvn_1, mean_1, sd_1) |> round(5)
    empirical_padded_bvn$p_2 <- pnorm(empirical_padded_bvn$x_bvn_2, mean_2, sd_2) |> round(5)
    empirical_padded_bvn$padding <- X
    empirical_padded_bvn$method <- "simple"
    
    return(empirical_padded_bvn)
  })

empirical_bvn_simple <- do.call(what = "rbind", empirical_bvn_simple) |>
  mutate(padding = factor(padding, levels = levels, labels = labels))
```

#### Edge Cases With Reference Distribution
```{r}
plot_simple_replacement <- plot_edge_cases(
  distribution,
  edge_cases_bvn_simple,
  title = "Simple Replacement"
)
plot_simple_replacement
```

#### Edge Cases With Empirical Data
```{r}
plot_simple_replacement <- plot_edge_cases(
  distribution = empirical_bvn_simple,
  edge_cases_bvn = edge_cases_bvn_simple,
  title = "Simple Replacement"
)
plot_simple_replacement
```


### Multiplicative Replacement
```{r}
# Edge Cases
edge_cases_bvn_multiplicative <-
  lapply(
    padding,
    FUN = function(X) {
      
      edge_cases_padded <- 
        multiplicative_replacement(edge_cases_raw, padding = X) |>
        as.data.frame()
      
      edge_cases_padded_bvn <- simplex_to_bvn(edge_cases_padded)
      edge_cases_padded_bvn$p_1 <- pnorm(edge_cases_padded_bvn$x_bvn_1, mean_1, sd_1) |>
        round(5)
      edge_cases_padded_bvn$p_2 <- pnorm(edge_cases_padded_bvn$x_bvn_2, mean_2, sd_2)|>
        round(5)
      edge_cases_padded_bvn$padding <- X
      edge_cases_padded_bvn$item <- rownames(edge_cases_raw) 
      edge_cases_padded_bvn$method <- "multiplicative"
      
      return(edge_cases_padded_bvn)
    }
  )

edge_cases_bvn_multiplicative <- do.call(what = "rbind", edge_cases_bvn_multiplicative) |>
  mutate(item = factor(item),
         padding = factor(
           padding,
           levels = levels,
           labels = labels
         ))

# Empirical Data
empirical_bvn_multiplicative <-
  lapply(
    padding,
    FUN = function(X) {
      empirical_padded <-
        multiplicative_replacement(empirical_raw, padding = X) |>
        as.data.frame()
      
      empirical_padded_bvn <- simplex_to_bvn(empirical_padded)
      empirical_padded_bvn$p_1 <- pnorm(empirical_padded_bvn$x_bvn_1, mean_1, sd_1) |>
        round(5)
      empirical_padded_bvn$p_2 <- pnorm(empirical_padded_bvn$x_bvn_2, mean_2, sd_2) |>
        round(5)
      empirical_padded_bvn$padding <- X
      empirical_padded_bvn$method <- "multiplicative"
      
      return(empirical_padded_bvn)
    }
  )

empirical_bvn_multiplicative <- do.call(what = "rbind", empirical_bvn_multiplicative) |>
  mutate(padding = factor(padding, levels = levels, labels = labels))
```


#### Edge Cases With Reference Distribution
```{r}
plot_multiplicative_replacement <- plot_edge_cases(
  distribution,
  edge_cases_bvn_multiplicative,
  title = "Multiplicative Replacement"
)
plot_multiplicative_replacement
```

#### Edge Cases With Empirical Data
```{r}
plot_multiplicative_replacement <- plot_edge_cases(
  distribution = empirical_bvn_multiplicative,
  edge_cases_bvn = edge_cases_bvn_multiplicative,
  title = "Multiplicative Replacement"
)
plot_multiplicative_replacement
```

  
### Rescaling
```{r}
# Edge Cases
edge_cases_bvn_rescaling <-
  lapply(
    padding,
    FUN = function(X) {
      edge_cases_padded <- 
        rescaling_replacement(edge_cases_raw, padding = X) |>
        as.data.frame()
      
      edge_cases_padded_bvn <- simplex_to_bvn(edge_cases_padded)
      edge_cases_padded_bvn$p_1 <- pnorm(edge_cases_padded_bvn$x_bvn_1, mean_1, sd_1) |>
        round(5)
      edge_cases_padded_bvn$p_2 <- pnorm(edge_cases_padded_bvn$x_bvn_2, mean_2, sd_2) |>
        round(5)
      edge_cases_padded_bvn$padding <- X
      edge_cases_padded_bvn$item <- rownames(edge_cases_raw) 
      edge_cases_padded_bvn$method <- "rescaling"
      
      return(edge_cases_padded_bvn)
    }
  )

edge_cases_bvn_rescaling <- do.call(what = "rbind", edge_cases_bvn_rescaling) |>
  mutate(item = factor(item),
         padding = factor(
           padding,
           levels = levels,
           labels = labels
         ))

# Empirical Data
empirical_bvn_rescaling <-
  lapply(
    padding,
    FUN = function(X) {
      empirical_padded <-
        rescaling_replacement(empirical_raw, padding = X) |>
        as.data.frame()
      
      empirical_padded_bvn <- simplex_to_bvn(empirical_padded)
      empirical_padded_bvn$p_1 <- pnorm(empirical_padded_bvn$x_bvn_1, mean_1, sd_1) |>
        round(5)
      empirical_padded_bvn$p_2 <- pnorm(empirical_padded_bvn$x_bvn_2, mean_2, sd_2) |>
        round(5)
      empirical_padded_bvn$padding <- X
      empirical_padded_bvn$method <- "rescaling"
      
      return(empirical_padded_bvn)
    }
  )
empirical_bvn_rescaling <- do.call(what = "rbind", empirical_bvn_rescaling) |>
  mutate(padding = factor(padding, levels = levels, labels = labels))
```

#### Edge Cases With Reference Distribution
```{r}
plot_rescaling_replacement <- plot_edge_cases(
  distribution,
  edge_cases_bvn_rescaling,
  title = "Rescaling Replacement"
)

plot_rescaling_replacement
```

#### Edge Cases With Empirical Data
```{r}
plot_rescaling_replacement <-
  plot_edge_cases(distribution = empirical_bvn_rescaling,
                  edge_cases_bvn = edge_cases_bvn_rescaling,
                  title = "Rescaling Replacement")
plot_rescaling_replacement
```


## Comparison of Methods

```{r}
edge_cases_bvn <- rbind(
  edge_cases_bvn_additive,
  edge_cases_bvn_simple,
  edge_cases_bvn_multiplicative,
  edge_cases_bvn_rescaling
) |> 
  mutate(method = factor(method)) 


empirical_bvn <- rbind(
  empirical_bvn_additive,
  empirical_bvn_simple,
  empirical_bvn_multiplicative,
  empirical_bvn_rescaling
) |> 
  mutate(method = factor(method))
```

#### Edge Cases With Reference Distribution
```{r}
plot_comparison_reference <- plot_edge_cases(
  distribution,
  edge_cases_bvn,
  title = "Comparison of Zero-Handling Methods"
) +
  facet_grid(padding ~ method) +
  theme_icm() +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(colour = "#6d6d6e", size = .3),
    axis.ticks = element_line(colour = "#6d6d6e", size = .3),
    axis.title.y = element_text(margin = margin(0, -5, 0, 0, "pt"))
  )
plot_comparison_reference

ggsave(
  here("plots", "comparison_zero_handling_reference.pdf"),
  plot_comparison_reference,
  width = 15,
  height = 15,
  units = "cm",
  scale = 1.8
)
```

#### Edge Cases With Empirical Data
```{r}
plot_comparison_empirical <- plot_edge_cases(
  distribution = empirical_bvn,
  edge_cases_bvn,
  title = "Comparison of Zero-Handling Methods"
) +
  facet_grid(padding ~ method) +
  theme_icm() +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(colour = "#6d6d6e", size = .3),
    axis.ticks = element_line(colour = "#6d6d6e", size = .3),
    axis.title.y = element_text(margin = margin(0, -5, 0, 0, "pt"))
  )
plot_comparison_empirical

ggsave(
  here("plots", "comparison_zero_handling_empirical.pdf"),
  plot_comparison_empirical,
  width = 15,
  height = 15,
  units = "cm",
  scale = 1.8
)
```


## Quantiles

```{r}

edge_cases_bvn |> dplyr::filter(p_1 < .01 & p_1 > .001) |> arrange(desc(p_1))
```

```{r}

edge_cases_bvn |> dplyr::filter(p_2 < .01 & p_2 > .001) |> arrange(desc(p_1))
```


```{r}

edge_cases_bvn |> dplyr::filter(p_2 > .99 & p_2 < .999) |> arrange(desc(p_1))
```

### Combinations of methods and padding that result in .01 > p > .001 for both dimensions
```{r}
edge_cases_bvn |> dplyr::filter((p_1 < .01 &
                      p_1 > .001 )|
                      (p_2 < .01 &
                      p_2 > .001) | (p_2 > .99 & p_2 < .999)) |> arrange(desc(p_1)) |> group_by(method, padding) |> 
  summarise(n = n()) |> dplyr::filter(n == 3)
```

# Ratios of components

```{r}
vec <- rbind(edge_cases_raw, E = c(.1,.8,.1), F = c(.1,.9,0))

vec
rescaling_replacement(vec, padding = .01)
simple_replacement(vec, padding = .01)
additive_replacement(vec, padding = .01)
multiplicative_replacement(vec, padding = .01)
```

```{r}
# function to compute ratios of components
compute_ratios <- function(simplex) {
  r1 <- simplex[, 1] / simplex[, 2]
  r2 <- simplex[, 2] / simplex[, 3]
  r3 <- simplex[, 1] / simplex[, 3]
  ratios <- cbind(r1, r2, r3)
  return(ratios)
}

vec2 <- vec[c("E", "F"), ]

cat("Ratios for original simplex:\n")
compute_ratios(vec2)

cat("\nRatios for rescaled simplex:\n")
compute_ratios(rescaling_replacement(vec2, padding = .01))

cat("\nRatios for simple replacement:\n")
compute_ratios(simple_replacement(vec2, padding = .01))

cat("\nRatios for additive replacement:\n")
compute_ratios(additive_replacement(vec2, padding = .01))

cat("\nRatios for multiplicative replacement:\n")
compute_ratios(multiplicative_replacement(vec2, padding = .01))
```


***

# Verbal Quantifiers: Sensitivity Analysis

## Process Item Names
```{r}
# item names
item_names_quantifier <- df_long %>%
  dplyr::select(jj, name_en) %>%
  distinct() %>%
  arrange(jj) %>%
  pull(name_en)
```

## Rescaling of Data
```{r}
#| code-fold: show

df_long <- df_long %>%
  dplyr::mutate(
    x_L_01 = (x_L / 100 + .01) / 1.03,
    x_U_01 = (x_U / 100 + .02) / 1.03,
    x_L_005 = (x_L / 100 + .005) / 1.015,
    x_U_005 = (x_U / 100 + .01) / 1.015,
    x_L_001 = (x_L / 100 + .001) / 1.003,
    x_U_001 = (x_U / 100 + .002) / 1.003
  )
```

## Stan Data
```{r}
### Stan data declaration
df_long <- df_long %>% dplyr::filter(!is.na(x_splx_1))

I = length(unique(df_long$ii))
J = length(unique(df_long$jj))
N  = nrow(df_long)
ii = df_long$ii
jj = df_long$jj
nn = c(1:N)

Y_splx_01 = cbind(
  df_long$x_L_01,
  df_long$x_U_01 - df_long$x_L_01,
  1 - df_long$x_U_01) |> 
  as.matrix()

Y_splx_005 = cbind(
  df_long$x_L_005,
  df_long$x_U_005 - df_long$x_L_005,
  1 - df_long$x_U_005) |> 
  as.matrix()

Y_splx_001 = cbind(
  df_long$x_L_001,
  df_long$x_U_001 - df_long$x_L_001,
  1 - df_long$x_U_001) |> 
  as.matrix()

#Y_splx[is.na(Y_splx)]

# # sanity check: all rows sum to 1
# check <- apply(Y_splx, 1, sum) %>% as.data.frame()
# table(check)

## stan data list
stan_data_01 <- list(
  I = I,
  J = J,
  N = N,
  ii = ii,
  jj = jj,
  nn = nn,
  Y_splx = Y_splx_01,
  padding = .01
)

stan_data_005 <- list(
  I = I,
  J = J,
  N = N,
  ii = ii,
  jj = jj,
  nn = nn,
  Y_splx = Y_splx_005,
  padding = .005
)

stan_data_001 <- list(
  I = I,
  J = J,
  N = N,
  ii = ii,
  jj = jj,
  nn = nn,
  Y_splx = Y_splx_001,
  padding = .001
)

# Choose model to fit
model_name <- "itm_quantifier_beta"
```

## Compile Model
```{r compile}
#| eval: !expr params$refit

# Compile model
model <-
  cmdstanr::cmdstan_model(
    stan_file = here("src", "models", paste0(model_name, ".stan")),
    pedantic = TRUE,
    quiet = FALSE
  )
```

## Fit Models
```{r fit generic, eval=FALSE}
#| eval: !expr params$refit

# number of MCMC chains
n_chains <- 4

# Run sampler
fit_01 <- model$sample(
  data = stan_data_01,
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 0,
  thin = 1,
  adapt_delta = .8,
  init = .1
)
# save fit
fit_01$save_object(file =  here("fits", paste0(model_name, "quantifier_sensitivity_01.RDS")))

# Run sampler
fit_005 <- model$sample(
  data = stan_data_005,
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 500,
  thin = 1,
  adapt_delta = .8,
  init = .1
)
# save fit
fit_005$save_object(file =  here("fits", paste0(model_name, "quantifier_sensitivity_005.RDS")))

# Run sampler
fit_001 <- model$sample(
  data = stan_data_001,
  seed = 2023,
  chains = n_chains,
  parallel_chains = n_chains,
  iter_warmup = 500,
  iter_sampling = 1000,
  refresh = 0,
  thin = 1,
  adapt_delta = .8,
  init = .1
)
# save fit
fit_001$save_object(file =  here("fits", paste0(model_name, "quantifier_sensitivity_001.RDS")))
```

```{r}
# load  fits
fit_01 <- readRDS(file =  here("fits", paste0(model_name, "quantifier_sensitivity_01.RDS")))
fit_005 <- readRDS(file =  here("fits", paste0(model_name, "quantifier_sensitivity_005.RDS")))
fit_001 <- readRDS(file =  here("fits", paste0(model_name, "quantifier_sensitivity_001.RDS")))
```

## Latent Consensus Intervals
```{r}
# Get posterior consensus intervals
consensus_01 <- data.frame(
  idx = 1:J,
  name = item_names_quantifier,
  Constant = ".01",
  lower_01 = fit_01$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[1:J],
  wid_01 = fit_01$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[(J +
                                                                             1):(J * 2)]
) %>%
  mutate(loc_01 = lower_01 + wid_01 / 2, upper_01 = lower_01 + wid_01) %>%
  arrange(lower_01)

consensus_005 <- data.frame(
  idx = 1:J,
  name = item_names_quantifier,
  Constant = ".005",
  lower_005 = fit_005$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[1:J],
  wid_005 = fit_005$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[(J +
                                                                             1):(J * 2)]
) %>%
  mutate(loc_005 = lower_005 + wid_005 / 2, upper_005 = lower_005 + wid_005) %>%
  arrange(lower_005)

consensus_001 <- data.frame(
  idx = 1:J,
  name = item_names_quantifier,
  Constant = ".001",
  lower_001 = fit_001$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[1:J],
  wid_001 = fit_001$summary("Tr_splx") %>% as.data.frame() %>% pull(median) %>% .[(J +
                                                                             1):(J * 2)]
) %>%
  mutate(loc_001 = lower_001 + wid_001 / 2, upper_001 = lower_001 + wid_001) %>%
  arrange(lower_001)

```


```{r}
colors <- c(".01" = "#d95f02", ".005" = "#7570b3", ".001" = "#1b9e77")

  ggplot() +
  geom_errorbarh(data = consensus_01, aes(x = loc_01, y = 1:J, xmin = lower_01, xmax = upper_01, col = ".01"), height = 0.3) +
  geom_errorbarh(data = consensus_005, aes(x = loc_005, y = 1:J + .3, xmin = lower_005, xmax = upper_005, col = ".005"), height = 0.3) +
  geom_errorbarh(data = consensus_001, aes(x = loc_001, y = 1:J + .6, xmin = lower_001, xmax = upper_001, col = ".001"), height = 0.3) +
  scale_x_continuous(
    limits = c(0, 1),
    labels = seq(0, 1, .25),
    expand = expansion()
  ) +
  scale_y_continuous(breaks = 1:J, labels = item_names_quantifier[consensus_01$idx]) +
  scale_color_manual(values = colors) +
    guides(color = guide_legend(reverse = TRUE)) +
  labs(x = "Latent Truth", y = NULL, col = "Padding Constant") +
  theme_icm(base_size = 16, hide_axis_text_y = F) +
  theme(
    #panel.grid = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.x = element_line(colour = "#6d6d6e")
  )

# save plot
ggsave(
  here("plots", "consensus_intervals_sensitivity.pdf"),
  width = 15,
  height = 10,
  units = "cm",
  scale = 1.3
)
ggsave(
  here("plots", "consensus_intervals_sensitivity.jpg"),
  width = 15,
  height = 10,
  units = "cm",
  scale = 1
)
```

Choosing a smaller padding constant, i.e., moving the extreme values for the intervals closer to zero and one, does not change the estimates for the consensus intervals in a substantively meaningful way. However, wider consensus intervals become a bit wider for the more extreme padding constant. In contrast, very narrow consensus intervals become a bit narrower. This is due to the fact that extreme values in the transformed space are exaggerated by stretching the scale more severely with the smaller padding constant.






